### 2015-09-22 p1/report/latex/draft.tex
added latex draft

\documentclass[11pt,english]{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{ {../} }

\author{Sean Curran \\
\and Stephen Durofchalk \\
\and Zachary Feldman \\
\and Ryan Wails}

\title{EE454 Project 1 Report}
\lstset{language=Matlab}
\renewcommand{\thesection}{\alph{section}}

\begin{document}
\maketitle

\newpage
\section{Project Summary}

\section{Procedural Approach}

\section{Experimental Observations}

\section{Performance Evaluation}

\section{Further Exploration}
\subsection{Test Cases}
To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the RNN.  Images were rescaled to thumbnail size (32x32x3) with the Matlab command
\begin{lstlisting}
thumbnail = imresize(img, [32 32]);
\end{lstlisting}

\noindent
110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.  Running these new 10 images through the RNN yielded the following results:\\

\begin{tabular}{ | c | c | c |}
  \hline
  Image \# & Image Contents & RNN Classification \\
  \hline		
  Image 1 & Tree in Field & Horse (8) \\
  Image 2 & Winter Mountain Scene & Ship (9) \\
  Image 3 & Ryan and Zach & Bird (3) \\
  Image 4 & Steve & Frog (7) \\
  Image 5 & Sean & Cat (4) \\
  Image 6 & Desktop Computer & Automobile (2) \\
  Image 7 & Football on Field & Deer(5) \\
  Image 8 & Robert Collins & Truck (10) \\
  Image 9 & Old Main & Bird(3) \\
  Image 10 & Penn State Logo & Truck (10)\\
  \hline  
\end{tabular}

\subsection{Reclassification}
An attempt was made to distinguish these 10 images from the rest of the data set (i.e. reclassify these 10 images as unknown).  Let $V$ be the vector of output probabilities from the RNN for each image.  Let $C$ be the classification of the image producing probability vector $V$.  Originally, we have\\~\\
\begin{math}
p_i \in V \\
p_{max} = \max(p_1, p_2,...,p_{10}) \\
C = i $ given $ p_i = p_{max}
\end{math}

~\newline\noindent
To reclassify the images we use\\
\noindent
\begin{math}
p_{max} = \max(p_1,p_2,...,p_{10}) \\
P = \{p_1,p_2,...,p_{10}\} \setminus \{p_{max}\} \\
p_{2max} = \max(P) \\~\\
\begin{cases}
C = i $ given $ p_i = p_{max} & $for	$ p_{max} - p_{2max} > 0.25 \\
C = 11 & $otherwise$
\end{cases}
\end{math}
~\\~\\
Less precisely, the difference between the two peak responses was thresholded by .25; so, if there were two strong responses, the image is reclassified as unknown.

\subsection{Results After Reclassification}
In the confusion matrix below, classes 1 through 10 are the same classifications.  Class 11 identifies an unknown image class. \\\\
\begin{tabular}{ | c | c | c | c | c | c | c | c | c | c | c | c | c | }
\hline
	 & CNN
Class & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ \hline
	True 
Class &  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
	1 &  & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 6 \\ \hline
	2 &  & 1 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 2 & 0 & 5 \\ \hline
	3 &  & 1 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 7 \\ \hline
	4 &  & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 9 \\ \hline
	5 &  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 & 9 \\ \hline
	6 &  & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 8 \\ \hline
	7 &  & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 8 \\ \hline
	8 &  & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 4 & 0 & 0 & 3 \\ \hline
	9 &  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 5 & 0 & 5 \\ \hline
	10 &  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 5 & 5 \\ \hline
	11 &  & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 9 \\ \hline
\end{tabular}

\includegraphics[scale=0.6]{confexp}
~\\~\\
\textbf{Accuracy = 29.09\%}
\\
The reclassification metric does well in replacing the 10 new images in the unknown category, but also places images that were previously correctly classified in the unknown category.  Other metrics tested were
\begin{enumerate}
\item Thresholding on the number of classes that had a response above 0.1 (the mean value for random classification)
\item Taking the spatial derivative of the probability vector; this metric actually produces zero-mean Gaussian noise with a very small standard deviation.
\end{enumerate}

\section{Member Contributions}

\end{document}

### 2015-09-23 p1/report/latex/draft.tex
added appendix for cnn output
RNN -> CNN

@@
 \usepackage{graphicx}
+\usepackage{morefloats}
+\usepackage[toc,page]{appendix}
 \graphicspath{ {../} }
@@
 
+\subsection{Intermediate Output}
+
+Included in the appendix attached to this report.
+
 \section{Performance Evaluation}
@@
 \subsection{Test Cases}
-To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the RNN.
+To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the CNN.
 Images were rescaled to thumbnail size (32x32x3) with the Matlab command
@@
 110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.
-Running these new 10 images through the RNN yielded the following results:\\
+Running these new 10 images through the CNN yielded the following results:\\
 
@@
 reclassify these 10 images as unknown).
-Let $V$ be the vector of output probabilities from the RNN for each image.
+Let $V$ be the vector of output probabilities from the CNN for each image.
 Let $C$ be the classification of the image producing probability vector $V$.
@@
 
+\newpage
+\begin{appendices}
+\section{Intermediate Output}
+
+\begin{figure}[h!]
+  \caption{Original Image}
+  \centering
+    \includegraphics[width=0.75\textwidth]{layer/0}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 1 Output}
+  \centering
+    \includegraphics[width=0.75\textwidth]{layer/1}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 2 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/2}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 3 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/3}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 4 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/4}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 5 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/5}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 6 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/6}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 7 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/7}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 8 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/8}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 9 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/9}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 10 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/10}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 11 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/11}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 12 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/12}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 13 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/13}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 14 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/14}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 15 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/15}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 16 Output}
+  \centering
+    \includegraphics[width=\textwidth]{layer/16}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 17 Output}
+  \centering
+    \includegraphics[width=0.75\textwidth]{layer/17}
+\end{figure}
+
+\begin{figure}[h!]
+  \caption{Layer 18 Output}
+  \centering
+    \includegraphics[width=0.75\textwidth]{layer/18}
+\end{figure}
+
+\end{appendices}
+
 \end{document}

### 2015-09-23 p1/report/latex/draft.tex
changed rnn to cnn
>=
dumb commit
small change to intermediate output section
1d Draft Added. Needs a little bit more work.

@@
 
-Included in the appendix attached to this report.
+Included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.
 
 \section{Performance Evaluation}
+\subsection{Results}
+	The following results were the outcome of classifying images as the class associated with the highest probability in the probability vector.
+\begin{center}
+	\includegraphics[scale=0.8]{confusionmatrix}
+	~\\~\\
+
+		Accuracy = 43.7\%
+\end{center}
+
+\begin{center}
+	\includegraphics[scale=0.7]{confsurf}
+	~\\~\\
+\end{center}
+\textbf{Discussion:}
+
+   The surface plot above demonstrates how well the CNN classifies images.
+There is a very strong response on the diagonal which represents the correct classifications.
+What is interesting is that this matrix is somewhat diagonal.
+This demonstrates that if images in a class of images $C_1$ are being confused for images in a class of images $C_2$, then images in $C_2$ are also being confused for images in $C_1$.
+A lot of this confusion is entirely logical; for example, trucks and automobiles are frequently confused for each other.
+Another great example of confusion are cats and dogs are frequently confused for one another.
+We are again very impressed with how well the CNN because it not only detects similarities between images within a class, but it detects similarities amongst images spanning multiple classes.
+
+    ~\\
+    \noindent
+    Note: The above results were produced using NeuralNet function located in 'NeuralNet.m'.
+
+\subsection{Looking at the Top-k Highest Probabilities}
+	The following subsection looks at how frequently an image's true class appears in one of the top-k ranked classes, as determined by probability scores sorted from highest to lowest.
+\begin{center}
+	\includegraphics[scale=0.8]{topktable}
+	Note: Accuracy is the percentage of times that the correct object class appeared in the top-k ranked classes, as determined by probability scores sorted form highest to lowest. 
+	~\\
+\end{center}
+\begin{center}
+	\includegraphics[scale=0.8]{topkplot}
+	~\\~\\
+\end{center}
+\textbf{Discussion:}
+      We were very surprised to see the top-k classification plot follow an exponential distribution.
+This demonstrates that the probability estimations provided by the CNN are accurate.
+We expected the probability estimations to be an arbitrary metric, but looking at the logarithmic nature of the plot it is clear that the probabilities are very accurate.
+
+	~\\
+	\noindent
+	Note: The above results were produced using the topk function located in 'topk.m' and NeuralNet function located in 'NeuralNet.m'.
 
@@
   \hline
-  Image \# & Image Contents & RNN Classification \\
+  Image \# & Image Contents & CNN Classification \\
   \hline		
@@
 \begin{cases}
-C = i $ given $ p_i = p_{max} & $for	$ p_{max} - p_{2max} > 0.25 \\
+C = i $ given $ p_i = p_{max} & $for	$ p_{max} - p_{2max} >= 0.25 \\
 C = 11 & $otherwise$

### 2015-09-23 p1/report/latex/draft.tex
continued discussion in intermediate output

@@
 
-Included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.
+Intermediate output generated by the CNN is included in the appendix attached to this report.
+Each figure shows the concatenated output of each layer as a gray scale image.
+The images can be produced by running `demo.m.'
+
+Observation of the output from each layer is consistent with the project description.
+Normalization produces an image with scaled pixel values but is relatively unchanged.
+Convolution produces a set of images with different feature sets extracted.
+The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).
+Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.
+Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.
 
@@
 
-		Accuracy = 43.7\%
+		\textbf{Accuracy = 43.7\%}
 \end{center}

### 2015-09-23 p1/report/latex/draft.tex
added source code for lst

@@
 \usepackage[toc,page]{appendix}
+\usepackage{color}
+
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+
 \graphicspath{ {../} }
@@
 
+\lstset{ %
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
+  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  breaklines=true,                 % sets automatic line breaking
+  captionpos=b,                    % sets the caption-position to bottom
+  commentstyle=\color{mygreen},    % comment style
+  deletekeywords={...},            % if you want to delete keywords from the given language
+  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
+  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
+  frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  keywordstyle=\color{blue},       % keyword style
+  language=Octave,                 % the language of the code
+  otherkeywords={*,...},            % if you want to add more keywords to the set
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+  showstringspaces=false,          % underline spaces within strings only
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  stringstyle=\color{mymauve},     % string literal style
+  tabsize=2,	                   % sets default tabsize to 2 spaces
+  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
+}
+
 \begin{document}
@@
 \section{Project Summary}
+
+\lstinputlisting[frame=single]{../../matlab/convolve.m}
 

### 2015-09-23 p1/report/latex/draft.tex
f

--- 2015-09-23 p1/report/latex/draft.tex
@@
 \usepackage[toc,page]{appendix}
+\usepackage{titlesec}
 \graphicspath{ {../} }
+
+\newcommand{\sectionbreak}{\clearpage}
 
@@
 
-Included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.
+Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.
 
@@
 \begin{center}
-	\includegraphics[scale=0.8]{confusionmatrix}
+	\includegraphics[scale=0.7]{confusionmatrix}
 	~\\~\\
@@
 \begin{center}
-	\includegraphics[scale=0.7]{confsurf}
+	\includegraphics[scale=0.6]{confsurf}
 	~\\~\\
@@
 
+~\\~\\
+\noindent
+Note: All of the exploratory images we used were either taken by us or were taken from Google Images.
+
 \subsection{Reclassification}
@@
 \section{Member Contributions}
+	Overall the contributions made form each team member were pretty even.
+Whenever the team met to work on the project most of the team members were in attendance.
+Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress.
+The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions.
+We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report.
+In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.
 

### 2015-09-23 p1/report/latex/draft.tex
More content and also changed some formatting.
Added content and each section starts on a new page now.

@@
 \noindent
-Note: All of the exploratory images we used were either taken by us or were taken from Google Images.
+All of the exploratory images we used were either taken by us or were taken from Google Images.
+The code we used to read in the exploratory images can be found in 'getAllFiles.m' and 'getTrueClass.m'.
+We produced the results above by running the 10 images through the function found in 'NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability.
+The classification process was done manually.
 
@@
 Less precisely, the difference between the two peak responses was thresholded by .25; so, if there were two strong responses, the image is reclassified as unknown.
-
+~\\~\\
+The code used to reclassify images can be found in 'identify\_exploratory.m'.
 \subsection{Results After Reclassification}
@@
 \end{enumerate}
+
+~\\~\\
+The code used to produce the results found in this section can be found in 'exploratory\_main.m'.
 

### 2015-09-23 p1/report/latex/draft.tex
added sections in project summary

--- 2015-09-23 p1/report/latex/draft.tex
@@
 \section{Project Summary}
+
+\subsection{Purpose}
+The purpose of this project was to implement a pre-trained convolutional neural network (CNN) using MATLAB.
+The CNN is composed of layers - each layer performs an operation on a set of input matrices and produces a corresponding output matrix.
+When these layers are composed together, they produce a network; the input of this network is an image, and the output of this network is a vector of classification probabilities.
+
+\subsection{Operations}
+
+\subsubsection{Image Normalization}
 

### 2015-09-23 p1/report/latex/draft.tex
fixed merge with master conflict in heading

@@
 
+\usepackage{titlesec}
 \graphicspath{ {../} }
+
+\newcommand{\sectionbreak}{\clearpage}
 
@@
 
+~\\~\\
+\noindent
+All of the exploratory images we used were either taken by us or were taken from Google Images.
+The code we used to read in the exploratory images can be found in 'getAllFiles.m' and 'getTrueClass.m'.
+We produced the results above by running the 10 images through the function found in 'NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability.
+The classification process was done manually.
+
 \subsection{Reclassification}
@@
 
+~\\~\\
+The code used to produce the results found in this section can be found in 'exploratory\_main.m'.
+
 \section{Member Contributions}
+	Overall the contributions made form each team member were pretty even.
+Whenever the team met to work on the project most of the team members were in attendance.
+Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress.
+The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions.
+We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report.
+In conclusion, the work was not split up evenly among our four group members, but everyone attempted to contribute.
 

### 2015-09-24 p1/report/latex/draft.tex
fix for adding layers

@@
 
+Image normalization takes each image and performs a linear scaling opera-
+tion on each pixel in the image. The result is an image where each pixel (in
+each channel) takes on a value in the range [-0.5 to 0.5].
+
+\lstinputlisting[frame=single]{../../matlab/ImNorm.m}
+
+\subsubsection{ReLU Layer}
+
+Rectification takes an input image and thresholds all the negative values to 0.  This layer emulates neurons with a particular activation function.
+
+\lstinputlisting[frame=single]{../../matlab/ReLU.m}
+
+\subsubsection{Pooling Layer}
+
+Pooling layers reduce variance in the image and reduce the overall size of the image by taking patches of the image and compressing that patch to a single pixel value.
+
+\lstinputlisting[frame=single]{../../matlab/Maxpool.m}
+
+\subsubsection{Convolutional Layer}
+
+The convolution operation takes a set of filters and bias values determined from the CNN's training phase and applies them over an image.
+The filter is applied with a convolution operator, and the bias is then added to every resultant pixel.
+
 \lstinputlisting[frame=single]{../../matlab/convolve.m}
+
+\subsubsection{Fully-Connected Layer}
+
+The fully-connected layer takes the output from the previous layer and maps it against every neuron in the network.  The output is a 1D vector of classifications (realized with soft max).
+
+\lstinputlisting[frame=single]{../../matlab/FuCd.m}
+
+\subsubsection{Soft Max Layer}
+
+The soft max layer takes the output from the fully-connected layer and maps it as input to a probability space.  Each probability in the output of soft max corresponds to a classification likelihood.
+
+\lstinputlisting[frame=single]{../../matlab/Softmax.m}
 

### 2015-09-24 p1/report/latex/draft.tex
Commit

--- 2015-09-23 p1/report/latex/draft.tex
@@
 \usepackage[toc,page]{appendix}
-\usepackage{color}
-
-\definecolor{mygreen}{rgb}{0,0.6,0}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mymauve}{rgb}{0.58,0,0.82}
-
 \usepackage{titlesec}
@@
 
-\lstset{ %
-  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
-  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
-  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
-  breaklines=true,                 % sets automatic line breaking
-  captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{mygreen},    % comment style
-  deletekeywords={...},            % if you want to delete keywords from the given language
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
-  frame=single,	                   % adds a frame around the code
-  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
-  keywordstyle=\color{blue},       % keyword style
-  language=Octave,                 % the language of the code
-  otherkeywords={*,...},            % if you want to add more keywords to the set
-  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
-  numbersep=5pt,                   % how far the line-numbers are from the code
-  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
-  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
-  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
-  showstringspaces=false,          % underline spaces within strings only
-  showtabs=false,                  % show tabs within strings adding particular underscores
-  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
-  stringstyle=\color{mymauve},     % string literal style
-  tabsize=2,	                   % sets default tabsize to 2 spaces
-  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
-}
-
 \begin{document}
@@
 \section{Project Summary}
-
-\subsection{Purpose}
-The purpose of this project was to implement a pre-trained convolutional neural network (CNN) using MATLAB.
-The CNN is composed of layers - each layer performs an operation on a set of input matrices and produces a corresponding output matrix.
-When these layers are composed together, they produce a network; the input of this network is an image, and the output of this network is a vector of classification probabilities.
-
-\subsection{Operations}
-
-\subsubsection{Image Normalization}
-
-\lstinputlisting[frame=single]{../../matlab/convolve.m}
 
@@
 
-Intermediate output generated by the CNN is included in the appendix attached to this report.
-Each figure shows the concatenated output of each layer as a gray scale image.
-The images can be produced by running `demo.m.'
-
-Observation of the output from each layer is consistent with the project description.
-Normalization produces an image with scaled pixel values but is relatively unchanged.
-Convolution produces a set of images with different feature sets extracted.
-The ReLu produces an image with a 0 threshold (MATLAB's imagesc command slightly changes the output image because the range of the pixel values in the image changes).
-Max Pooling reduces the size of the image by a factor of (nxn) and has the effect of making the previous image look more ``blocky'' via down-sampling.
-Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.
+Intermediate output generated by the CNN is included in the appendix attached to this report.  Each figure shows the concatenated output of each layer as a gray scale image.
 
@@
 
-		\textbf{Accuracy = 43.7\%}
+		Accuracy = 43.7\%
 \end{center}
@@
 	\includegraphics[scale=0.8]{topktable}
+
+\end{center}
 	Note: Accuracy is the percentage of times that the correct object class appeared in the top-k ranked classes, as determined by probability scores sorted form highest to lowest. 
 	~\\
-\end{center}
 \begin{center}
@@
 \textbf{Discussion:}
-      We were very surprised to see the top-k classification plot follow an exponential distribution.
+      We were very surprised to see the top-k classification plot follow a logarithmic distribution.
 This demonstrates that the probability estimations provided by the CNN are accurate.
-We expected the probability estimations to be an arbitrary metric, but looking at the logarithmic nature of the plot it is clear that the probabilities are very accurate.
+We expected the probability estimations to be an arbitrary metric, used to find reasonable classification for an image, but looking at the logarithmic nature of the plot it is clear that the probabilities are very accurate.
+In fact, when looking at the probabilities for the 10,000 images you will find that on average an images top-k probabilities sum up to the y value shown above.
+For example, the average max probabilities for the 10,00 images is .4425 and 43.71\% of the time the max probability is correct.
+Even more interesting, the average of the top 2 probabilities added together for each image is .6646 and the chance of the true class being associated with one of the top two highest probabilities in its probability vector .6591, as shown above.
 

### 2015-09-24 p1/report/latex/draft.tex
added code for a

--- 2015-09-24 p1/report/latex/draft.tex
@@
 \usepackage{color}
+\usepackage{pdfpages}
 
@@
 \section{Procedural Approach}
+
+\subsection{Design Discussion}
+
+There was a general design that we collectively decided would be the best approach to attacking the recreation of the Convolutional Neural Network.
+This was a bottom up design.
+Working from the bottom we created the features of the CNN first.
+These features being the fundamental layers an image would be filtered through after being broken down through normalization and convolution.
+Once these features were established we then looked upwards towards a more directed approach of connecting them together to form the desired filtered network.
+Because we were given a table of the path of the network this step was easy to implement.
+The output of one layer feature became the input of another and so on.
+At this point the network was wrapped into a higher layer structure that was dynamic in nature.
+Acting like a black box function given an array of images and set of parameters a matrix output of probabilities could be produced.
+
+Design implementations were also taken closely into consideration.
+Our Matlab coding reflects procedural programming more commonly found in the C language.
+This was done in creating supporting files, functional programming, and nested for loop structures.
+A few of the supporting files consisted of the convolve, the ReLU, and the maxpool function.
+Function calls in the neuralNet script called to these functions passing the necessary parameters along with it.
+These functions are much like functional programming in c++ where the purpose is to have a module or block of program code that handles a particular task.
+These modules come in handy for being reusable.
+By implementing this into our neural net we are able to greatly reduce the number of lines in our code while at the same time making it more robust.
+We have assurance in the function that when we call that section of code to handle a specific job it will stand by itself.
+Digging deeper into these function modules there was also some design implementation at a lower level.
+In the project description under the basic operations all of the computational building blocks defined using summations.
+For example in fully connected the output is determined by summations in all dimensions of the image including the rows columns and channels.
+We extracted this summation notation and created nested for loop structures to handle looping through all iterations of the dimensions and computing the summations in a totaling type of way.
+In fact the for loop structure was used throughout the project even in the neuralNet code.
+It was decided that the for loop be used here for the vast amount of images that have to be run through the CNN to produce the probability vectors.
+
+As a group few deviations from the project description were taken.
+The only noticeable deviations were towards the end in the grading section in which the questions were done out of order.
+For instance we partook on the exploratory mode of section 1e before testing some of the required performance evaluations.
+
+\newpage
+\includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}
 

### 2015-09-24 p1/report/latex/draft.tex
Small Correctinos

@@
 \\
-The reclassification metric does well in replacing the 10 new images in the unknown category, but also places images that were previously correctly classified in the unknown category.
-Other metrics tested were
+The reclassification metric does well in placing the 10 new images in the unknown category, but it also incorrectly classifies many images as unknown.  Other metrics tested were:
 \begin{enumerate}

### 2015-09-24 p1/report/latex/draft.tex
idk

--- 2015-09-24 p1/report/latex/draft.tex
@@
 When these layers are composed together, they produce a network; the input of this network is an image, and the output of this network is a vector of classification probabilities.
+
+Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.
 
@@
 We extracted this summation notation and created nested for loop structures to handle looping through all iterations of the dimensions and computing the summations in a totaling type of way.
-In fact the for loop structure was used throughout the project even in the neuralNet code.
+In fact the for loop structure was used throughout the project even in the Neural Net code.
 It was decided that the for loop be used here for the vast amount of images that have to be run through the CNN to produce the probability vectors.

### 2015-09-24 p1/report/latex/draft.tex
added a bit more to a
Finalish Draft

--- 2015-09-24 p1/report/latex/draft.tex
@@
 
-\subsection{Design Discussion}
+\subsection{Overview}
 
-There was a general design that we collectively decided would be the best approach to attacking the recreation of the Convolutional Neural Network.
-This was a bottom up design.
-Working from the bottom we created the features of the CNN first.
-These features being the fundamental layers an image would be filtered through after being broken down through normalization and convolution.
-Once these features were established we then looked upwards towards a more directed approach of connecting them together to form the desired filtered network.
-Because we were given a table of the path of the network this step was easy to implement.
-The output of one layer feature became the input of another and so on.
-At this point the network was wrapped into a higher layer structure that was dynamic in nature.
-Acting like a black box function given an array of images and set of parameters a matrix output of probabilities could be produced.
-
-Design implementations were also taken closely into consideration.
-Our Matlab coding reflects procedural programming more commonly found in the C language.
-This was done in creating supporting files, functional programming, and nested for loop structures.
-A few of the supporting files consisted of the convolve, the ReLU, and the maxpool function.
-Function calls in the neuralNet script called to these functions passing the necessary parameters along with it.
-These functions are much like functional programming in c++ where the purpose is to have a module or block of program code that handles a particular task.
-These modules come in handy for being reusable.
-By implementing this into our neural net we are able to greatly reduce the number of lines in our code while at the same time making it more robust.
-We have assurance in the function that when we call that section of code to handle a specific job it will stand by itself.
-Digging deeper into these function modules there was also some design implementation at a lower level.
-In the project description under the basic operations all of the computational building blocks defined using summations.
-For example in fully connected the output is determined by summations in all dimensions of the image including the rows columns and channels.
-We extracted this summation notation and created nested for loop structures to handle looping through all iterations of the dimensions and computing the summations in a totaling type of way.
-In fact the for loop structure was used throughout the project even in the neuralNet code.
-It was decided that the for loop be used here for the vast amount of images that have to be run through the CNN to produce the probability vectors.
-
-As a group few deviations from the project description were taken.
-The only noticeable deviations were towards the end in the grading section in which the questions were done out of order.
-For instance we partook on the exploratory mode of section 1e before testing some of the required performance evaluations.
+This section will highlight some of the key design decisions we made and will try to provide some insight on why we made said decisions.
+First and foremost, we decided to make the CNN modular in-order to facilitate code re-usage.
+For example, we only wrote one convolution function that is reused 9 times throughout the CNN.
+The decision to modularize the CNN and make functions general allowed us to be more productive while insuring that our code was correct.
+It is also worth noting that this design decision forced us to work in a bottom-up manner.
 
@@
 \includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}
+
+\subsection{Diving a Little Deeper}
+In almost every function we chose C-like code as opposed to using linear algebra to accomplish the same tasks.
+We choose to use C-like code because that was by far more natural to all of us.
+We also choose to make some of our functions as general as possible so they could be used outside of the CNN.
+For example, we were able to reuse the 'NeuralNet' function on the images we gathered from the Internet because it was not reliant on specifics such as the number of images being passed through the CNN.
 

### 2015-09-24 p1/report/latex/draft.tex
fixed quote direction

--- 2015-09-24 p1/report/latex/draft.tex
@@
 Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.
+The test images provided also have ground-truth classifications; so, we can compare the results of the CNN with the ground truth labels to obtain a measure of accuracy.
 
@@
 \end{lstlisting}
-
 \noindent
@@
 All of the exploratory images we used were either taken by us or were taken from Google Images.
-The code we used to read in the exploratory images can be found in 'getAllFiles.m' and 'getTrueClass.m'.
-We produced the results above by running the 10 images through the function found in 'NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability.
+The code we used to read in the exploratory images can be found in `getAllFiles.m' and `getTrueClass.m'.
+We produced the results above by running the 10 images through the function found in `NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability.
 The classification process was done manually.

### 2015-09-24 p1/report/latex/draft.tex
Fixed Comma
polish

--- 2015-09-24 p1/report/latex/draft.tex
@@
 
+Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.
+The test images provided also have ground-truth classifications; so, we can compare the results of the CNN with the ground truth labels to obtain a measure of accuracy.
+
 \subsection{Operations}
@@
 
-\newpage
-\includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}
-
 \subsection{Diving a Little Deeper}
@@
 For example, we were able to reuse the 'NeuralNet' function on the images we gathered from the Internet because it was not reliant on specifics such as the number of images being passed through the CNN.
+
+\includepdf[pages={1}]{../FlowChart_pdf_1b.pdf}
 
@@
 
+\subsection{Visual Verification}
+
 Observation of the output from each layer is consistent with the project description.
-Normalization produces an image with scaled pixel values but is relatively unchanged.
+Normalization produces an image with scaled pixel values, but is relatively unchanged.
 Convolution produces a set of images with different feature sets extracted.
@@
 Finally, we have the fully-connected layer and the soft max layer which produce a vector of classification probabilities from the image which are represented by the bar graph.
+
+\subsection{Analytical Verification}
+Passing the test image provided through our Neural Net produces the following probability vector:\\~\\
+\begin{tabular}{| c | c | c | c | c | c | c | c | c | c |}
+\hline
+0.525 & 0.004 & 0.067 & 0.120 & 0.018 & 0.019 & 0.014 & 0.009 &	0.210 & 0.010 \\
+\hline
+\end{tabular}
+
+~\\ This probability vector is the same as the probability vector provided in the test data (and indicates a correct classification of airplane).
+While not rigorous proof, this result is indicative of correctness.
+Additionally, at every layer of the CNN, we verified that the test layer output provided was the same as the output produced by our Neural Net.
 
@@
 \section{Member Contributions}
-	Overall the contributions made form each team member were pretty even.
+	Overall the contributions made from each team member were pretty even.
 Whenever the team met to work on the project most of the team members were in attendance.
 Everyone who was in attendance at each team meeting attempted to work on a different piece of the project to ensure that we were making steady progress.
-The coding was not split up evenly as one team member did not attend the initial meeting and as a result he missed most of the actual coding and basically all of the design decisions.
+The coding was not split up completely evenly: much of the coding work was tasked by layer, and each layer did not constitute the same amount of work.
 We attempted to split the report up evenly, but as the deadline approached scheduling meetings became difficult and some individuals were unavailable to work on the report.

### 2015-12-10 p2/matlab/ransac.m
ransac tested and working

@@ -1,12 +1,13 @@
-function [bestTX,bestTY] = ransac(data1,data2,numPoints,iterations,thresholdDistance,inlierRatio)
+function [bestTX,bestTY] = ransac(data1,data2,iterations,thresholdDistance,inlierRatio)
 	bestTX = 0;
 	bestTY = 0;
 	bestNumInliers = 0;
-	numDataPoints = size(data, 2);
+	numDataPoints = size(data1, 2);
 	for i=1:iterations
 		numInliers = 0;
 		% grab 1 random pair of matching points
-		randIndex = randi([1 numDataPoints],1,1);	% random number between 1 and numDataPoints
+        % random number between 1 and numDataPoints
+		randIndex = randi([1 numDataPoints],1,1);	
 		randDataPoint1 = data1(:,randIndex);
 		randDataPoint2 = data2(:,randIndex);
 		
@@ -23,17 +24,19 @@ function [bestTX,bestTY] = ransac(data1,data2,numPoints,iterations,thresholdDist
 		
 		% loop through all data points
 		for j=1:numDataPoints
-			xpred = data1(1,j) + tx;
-			ypred = data1(2,j) + ty;
-			xreal = data2(1,j);
-			yreal = data2(2,j);
+			x_pred = data1(1,j) + tx;
+			y_pred = data1(2,j) + ty;
+			x_real = data2(1,j);
+			y_real = data2(2,j);
 			
-			% calculate distance from the predicted location of this point to its actual location
-			distance = sqrt((xpred - xreal)^2 + (ypred - yreal)^2);
+			% calculate distance from the predicted location ...
+            % of this point to its actual location
+			distance = sqrt((x_pred - x_real)^2 + (y_pred - y_real)^2);
 			if (distance <= thresholdDistance)
-				numInliers++;
+				numInliers = numInliers+1;
 		end	
-		if (numInliers >= (inlierRatio * numDataPoints) && numInliers > bestNumInliers)
+		if (numInliers >= (inlierRatio * numDataPoints) ...
+                && numInliers > bestNumInliers)
 			bestNumInliers = numInliers;
 			bestTX = tx;
 			bestTY = ty;

### 2015-12-10 p2/matlab/harris_tb.m
added harris_tb and test img

@@ -1,0 +1,19 @@
+
+test = imread('test.jpg');
+harris_img = harris(test, 1, 640, 1, 445);
+
+d=linspace(min(harris_img(:)),max(harris_img(:)),256);
+im_s = uint8(arrayfun(@(x) find(abs(d(:)-x)== min(abs(d(:)-x))), harris_img));
+% bw = im_s < 150;
+bw = imcomplement(bw);
+
+% harris_img = im2bw(harris_img, 0.5);
+colormap(gray);
+imagesc(test);
+
+% s = regionprops(bw, 'Centroid');
+% hold on;
+% for k = 1:numel(s)
+%     plot(s(k).Centroid(1), s(k).Centroid(2), 'r*')
+% end
+% hold off;

### 2015-12-11 p2/matlab/blob2px.m
harris blob example

@@ -1,0 +1,30 @@
+function [ output_args ] = blob2px( img, threshold )
+%BLOB2PX Takes an intensity image and computes blob centroids.
+%   img:            The intensity image.
+%   threshold:      Amount of thesholding to perform. Range [1-255]
+%   output_args:    Array containing pixel locations of corners.
+%                   First elem is row idx, second elem is col idx.
+
+output_args = [];
+
+% Image scaling code adopted from:
+% http://www.mathworks.com/matlabcentral/answers/66406-how-to-convert-a-double-matrix-image-to-a-unit8-matrix
+d = linspace(min(img(:)),max(img(:)),256);
+img_scaled = uint8(arrayfun(@(x) find(abs(d(:)-x)== min(abs(d(:)-x))), img));
+
+bw_img = img_scaled < threshold;
+bw_img = imcomplement(bw_img);
+
+imagesc(bw_img);
+sum(sum(bw_img))
+s = regionprops(bw_img, 'Centroid');
+
+for k = 1 : numel(s)
+    px = zeros(2,1);
+    px(1,1) = s(k).Centroid(1);
+    px(2,1) = s(k).Centroid(2);
+    output_args = [output_args px];
+end
+
+end
+

### 2015-12-11 p2/matlab/harris_blob_example.m

@@ -1,0 +1,12 @@
+
+sample = imread('../frames/DaMultiview-seq7022.png');
+harris_img = harris(sample, 90, 140, 100, 300);
+colormap(gray);
+corners = blob2px(harris_img, 50);
+
+image(sample);
+hold on;
+for k = 1 : numel(corners) / 2
+    plot(corners(1,k), corners(2,k), 'r*');
+end
+hold off;

### 2015-12-11 p2/matlab/harris_tb.m

@@ -4,12 +4,12 @@ harris_img = harris(test, 1, 640, 1, 445);
 
 d=linspace(min(harris_img(:)),max(harris_img(:)),256);
 im_s = uint8(arrayfun(@(x) find(abs(d(:)-x)== min(abs(d(:)-x))), harris_img));
-% bw = im_s < 150;
-bw = imcomplement(bw);
+bw = im_s < 150;
+bw = imcomplement(im_s);
 
 % harris_img = im2bw(harris_img, 0.5);
 colormap(gray);
-imagesc(test);
+imagesc(bw);
 
 % s = regionprops(bw, 'Centroid');
 % hold on;

### 2015-12-11 p2/matlab/harris_blob_example.m
fixed harris blob example

@@ -2,9 +2,9 @@
 sample = imread('../frames/DaMultiview-seq7022.png');
 harris_img = harris(sample, 90, 140, 100, 300);
 colormap(gray);
-corners = blob2px(harris_img, 50);
+imagesc(harris_img);
+corners = blob2px(harris_img, 45);
 
-image(sample);
 hold on;
 for k = 1 : numel(corners) / 2
     plot(corners(1,k), corners(2,k), 'r*');

### 2015-12-11 p2/matlab/blob2px.m
added monte carlo filtering

@@ -1,7 +1,8 @@
-function [ output_args ] = blob2px( img, threshold )
+function [ output_args ] = blob2px( img, threshold, alpha )
 %BLOB2PX Takes an intensity image and computes blob centroids.
 %   img:            The intensity image.
 %   threshold:      Amount of thesholding to perform. Range [1-255]
+%   alpha:          Percent of blob to consider a corner.
 %   output_args:    Array containing pixel locations of corners.
 %                   First elem is row idx, second elem is col idx.
 
@@ -14,6 +15,8 @@ img_scaled = uint8(arrayfun(@(x) find(abs(d(:)-x)== min(abs(d(:)-x))), img));
 
 bw_img = img_scaled < threshold;
 bw_img = imcomplement(bw_img);
+
+bw_img = pruneMatrix(bw_img, alpha);
 
 s = regionprops(bw_img, 'Centroid');
 

### 2015-12-11 p2/matlab/harris_blob_example.m

@@ -3,7 +3,7 @@ sample = imread('../frames/DaMultiview-seq7022.png');
 harris_img = harris(sample, 90, 140, 100, 300);
 colormap(gray);
 imagesc(harris_img);
-corners = blob2px(harris_img, 45);
+corners = blob2px(harris_img, 45, 0.05);
 
 hold on;
 for k = 1 : numel(corners) / 2

### 2015-12-11 p2/matlab/pruneMatrix.m

@@ -1,0 +1,12 @@
+function [ out ] = pruneMatrix( x, alpha )
+%PRUNEMATRIX 
+
+out = x;
+
+for k = 1 : numel(out)
+    if (rand() > alpha)
+        out(k) = 0;
+    end
+end
+
+end

### 2015-12-11 p2/matlab/main.m
changed zach's code to use array of cells

@@ -1,7 +1,7 @@
 
 clc
 %fill gtboxarray which has window information ie. max's and min's
-parseGroundTruth;
+parseGroundTruthSupressed;
 
 numOfFrames = 3; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
@@ -13,32 +13,3 @@ alpha = 0.15;
 
 matchVals = phase1(numOfFrames, frameSkipRate, frameindex, gtboxarray, filenameArr, sFrameArr, threshold, alpha);
 
-%boxes %corners
-%{
-i1[][]
-i2[][]
-i1boxes
-i2boxes
-cornerpatchx
-cornerpatchy
-%match up corners
-    boxmatchmatrix = zeros(i1boxes,i2boxes);
-    for b1 = 1:i1boxes
-        for b2 = 1:i2boxes
-            i1corners
-            i2corners
-            cornermatchmatrix = zeros(i1corner,i2corners);
-            for c1 = 1:i1corners
-               for c2 = 1:i2corners
-                    ssd = SumOfSquareDifferences(i1(b1,c1),i2(b2,c2),...
-                        cornerpatchx,cornerpatchy);
-                    cornermatchmatrix(c1,c2) = ssd;
-               end
-            end
-            [acorners,ccorners] = assignmentoptimal(cornermatchmatrix);
-            boxmatchmatrix(b1,b2) = ccorners;
-        end
-    end
-    [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
-    
- %}   

### 2015-12-11 p2/matlab/parseGroundTruthSupressed.m

@@ -1,0 +1,32 @@
+%sample data for Project 2
+
+%reading in the ground truth xml file
+%and storing info in an array
+
+gtboxarray = [];
+
+foo = xml2struct('../xml/TUD-Stadtmitte.xml');
+frames = foo.dataset.frame;
+
+numframes = length(frames);
+for findex = 1:numframes
+    frame = frames{findex};
+    fnum = sscanf(frame.Attributes.number,'%d');
+    objects = frame.objectlist.object;
+    numobjects = length(objects);
+    for oindex = 1:numobjects
+        id = sscanf(objects{oindex}.Attributes.id,'%d');
+        boxAtt = objects{oindex}.box.Attributes;
+        h = sscanf(boxAtt.h,'%f');
+        w = sscanf(boxAtt.w,'%f');
+        xc = sscanf(boxAtt.xc,'%f');
+        yc = sscanf(boxAtt.yc,'%f');        
+        xmin = floor(xc-w/2);
+        ymin = floor(yc-h/2);
+        xmax = ceil(xc+w/2);
+        ymax = ceil(yc+h/2);
+        gtboxarray(end+1,:) = [fnum id xmin ymin xmax ymax];
+    end 
+end
+
+

### 2015-12-11 p2/matlab/phase1.m

@@ -1,4 +1,7 @@
 function [output, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex, gtboxarray, filenameArr, sFrameArr, threshold, alpha)
+   
+    output = [];
+
     filepath = '../frames/DaMultiview-seq';
    for n = 1:numOfFrames
         if frameindex < 7200  %make sure number of trials and skip rate doesnt exceed highest indexed frame
@@ -36,16 +39,16 @@ function [output, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex, gt
             %disp(gtboxarray(tempIndex,2));
             %windowNumber = gtboxarray(tempIndex,2);
             %scan rest of frames for matching window number
-            disp(gtboxarray(tempIndex,2));
+            % disp(gtboxarray(tempIndex,2));
             tXmin = gtboxarray(tempIndex,3);
             tXmax = gtboxarray(tempIndex,5);
             tYmin = gtboxarray(tempIndex,4);
             tYmax = gtboxarray(tempIndex,6);
-            disp(tYmax);
+            % disp(tYmax);
             str = char(filenameArr(n)); %convert cell to string
             image = imread(str);
             img = harris(image,tXmin,tXmax,tYmin,tYmax);
-            output = blob2px( img, threshold, alpha );
+            output = [output { blob2px( img, threshold, alpha ) }];
             tempIndex = tempIndex + 1;
         end
     end

### 2015-12-11 p2/matlab/SumOfSqaureDifferences.m
barf matcher is "done"

@@ -1,9 +1,14 @@
-function [ ssd ] = SumOfSqaureDifferences( p1,p2,x,y )
+function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
     ssd = 0;
-
+    
+    p1(1) = p1(1)-y/2;
+    p1(2) = p1(2)-x/2;
+    p2(1) = p2(1)-y/2;
+    p2(2) = p2(2)-x/2;
     for i=1:x
       for j=1:y
-        ssd = ssd + (p1(i,j)-p2(i,j))^2;
+        ssd = ssd + (i1(w1(4)+p1(1)+j,w1(3)+p1(2)+i)...
+            -i2(w2(4)+p2(1)+j,w2(3)+p2(2)+i))^2;
       end
     end
 end

### 2015-12-11 p2/matlab/main.m

@@ -23,6 +23,7 @@ for n = 1:numOfFrames
         filenameArr{end+1} = filename;
         disp(filenameArr(n));
         image = imread(filename);
+        
     
         %search for desired frames
         r = 1;
@@ -90,32 +91,6 @@ end
 
 
 
-%boxes %corners
-%{
-i1[][]
-i2[][]
-i1boxes
-i2boxes
-cornerpatchx
-cornerpatchy
-%match up corners
-    boxmatchmatrix = zeros(i1boxes,i2boxes);
-    for b1 = 1:i1boxes
-        for b2 = 1:i2boxes
-            i1corners
-            i2corners
-            cornermatchmatrix = zeros(i1corner,i2corners);
-            for c1 = 1:i1corners
-               for c2 = 1:i2corners
-                    ssd = SumOfSquareDifferences(i1(b1,c1),i2(b2,c2),...
-                        cornerpatchx,cornerpatchy);
-                    cornermatchmatrix(c1,c2) = ssd;
-               end
-            end
-            [acorners,ccorners] = assignmentoptimal(cornermatchmatrix);
-            boxmatchmatrix(b1,b2) = ccorners;
-        end
-    end
-    [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
+
     
- %}   
+    

### 2015-12-11 p2/matlab/main_BACKUP_828.m
cleaning up

@@ -1,101 +1,0 @@
-
-clc
-%fill gtboxarray which has window information ie. max's and min's
-parseGroundTruthSupressed;
-
-numOfFrames = 3; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7022;  %starting frame; range is 7024-7200s
-filenameArr = {}; %filenames for selected frames 
-sFrameArr = [];    %starting indexes of selected frame for gtboxarray
-threshold = 40;
-alpha = 0.15;
-
-matchVals = phase1(numOfFrames, frameSkipRate, frameindex, gtboxarray, filenameArr, sFrameArr, threshold, alpha);
-
-<<<<<<< HEAD
-%fill file name array and find the starting rows for frames in the
-%gtboxarray (this array holds all bounding box data for every window in
-%each frame
-for n = 1:numOfFrames
-    if frameindex < 7200  %make sure number of trials and skip rate doesnt exceed highest indexed frame
-        filename = strcat(filepath, num2str(frameindex));
-        
-        filename = strcat(filename, '.png');
-        %disp(filename);
-        filenameArr{end+1} = filename;
-        disp(filenameArr(n));
-        image = imread(filename);
-        
-    
-        %search for desired frames
-        r = 1;
-        while(frameindex ~= gtboxarray(r,1))
-            %disp(gtboxarray(r,1));
-            r = r + 1;
-        end
-        sFrameArr = [sFrameArr r];  %starting index of data for image in gtboxarray
-        disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
-        
-        frameindex = frameindex + frameSkipRate;
-    end
-end
-
-%run harris corner and get corners for each window
-%window is defined by column 2 in gtboxarray
-%below code identifies which windows are shared between all selected frames
-%if there is a common window then it runs harris on this window from each
-%frame
-message2 = 'running harris corners of matching windows of all frames:';
-disp(message2);
-firstFrameNum = gtboxarray(sFrameArr(1),1);
-tempIndex = sFrameArr(1);
-%disp(tempFrameNum);
-while(gtboxarray(tempIndex,1) == firstFrameNum)
-    %disp(gtboxarray(tempIndex,2));
-    windowNumber = gtboxarray(tempIndex,2);
-    %scan rest of frames for matching window number
-    match = [];
-    for p = 2:length(filenameArr)
[…]

### 2015-12-11 p2/matlab/main_BASE_828.m

@@ -1,121 +1,0 @@
-clear
-clc
-%fill gtboxarray which has window information ie. max's and min's
-parseGroundTruth;
-
-numOfFrames = 2; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7022;  %starting frame; range is 7024-7200
-filepath = '../frames/DaMultiview-seq';
-filenameArr = {}; %filenames for selected frames 
-sFrameArr = [];    %starting indexes of selected frame for gtboxarray
-
-
-%fill file name array and find the starting rows for frames in the
-%gtboxarray (this array holds all bounding box data for every window in
-%each frame
-for n = 1:numOfFrames
-    if frameindex < 7200  %make sure number of trials and skip rate doesnt exceed highest indexed frame
-        filename = strcat(filepath, num2str(frameindex));
-        
-        filename = strcat(filename, '.png');
-        %disp(filename);
-        filenameArr{end+1} = filename;
-        disp(filenameArr(n));
-        image = imread(filename);
-    
-        %search for desired frames
-        r = 1;
-        while(frameindex ~= gtboxarray(r,1))
-            %disp(gtboxarray(r,1));
-            r = r + 1;
-        end
-        sFrameArr = [sFrameArr r];  %starting index of data for image in gtboxarray
-        disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
-        
-        frameindex = frameindex + frameSkipRate;
-    end
-end
-
-%run harris corner and get corners for each window
-%window is defined by column 2 in gtboxarray
-%below code identifies which windows are shared between all selected frames
-%if there is a common window then it runs harris on this window from each
-%frame
-message2 = 'running harris corners of matching windows of all frames:';
-disp(message2);
-firstFrameNum = gtboxarray(sFrameArr(1),1);
-tempIndex = sFrameArr(1);
-%disp(tempFrameNum);
-while(gtboxarray(tempIndex,1) == firstFrameNum)
-    %disp(gtboxarray(tempIndex,2));
-    windowNumber = gtboxarray(tempIndex,2);
-    %scan rest of frames for matching window number
-    match = [];
-    for p = 2:length(filenameArr)
-        tempFrameNum = gtboxarray(sFrameArr(p),1);
-        subIndex = sFrameArr(p);
[…]

### 2015-12-11 p2/matlab/main_LOCAL_828.m

@@ -1,96 +1,0 @@
-clear
-clc
-%fill gtboxarray which has window information ie. max's and min's
-parseGroundTruth;
-
-numOfFrames = 2; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7022;  %starting frame; range is 7024-7200
-filepath = '../frames/DaMultiview-seq';
-filenameArr = {}; %filenames for selected frames 
-sFrameArr = [];    %starting indexes of selected frame for gtboxarray
-
-
-%fill file name array and find the starting rows for frames in the
-%gtboxarray (this array holds all bounding box data for every window in
-%each frame
-for n = 1:numOfFrames
-    if frameindex < 7200  %make sure number of trials and skip rate doesnt exceed highest indexed frame
-        filename = strcat(filepath, num2str(frameindex));
-        
-        filename = strcat(filename, '.png');
-        %disp(filename);
-        filenameArr{end+1} = filename;
-        disp(filenameArr(n));
-        image = imread(filename);
-        
-    
-        %search for desired frames
-        r = 1;
-        while(frameindex ~= gtboxarray(r,1))
-            %disp(gtboxarray(r,1));
-            r = r + 1;
-        end
-        sFrameArr = [sFrameArr r];  %starting index of data for image in gtboxarray
-        disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
-        
-        frameindex = frameindex + frameSkipRate;
-    end
-end
-
-%run harris corner and get corners for each window
-%window is defined by column 2 in gtboxarray
-%below code identifies which windows are shared between all selected frames
-%if there is a common window then it runs harris on this window from each
-%frame
-message2 = 'running harris corners of matching windows of all frames:';
-disp(message2);
-firstFrameNum = gtboxarray(sFrameArr(1),1);
-tempIndex = sFrameArr(1);
-%disp(tempFrameNum);
-while(gtboxarray(tempIndex,1) == firstFrameNum)
-    %disp(gtboxarray(tempIndex,2));
-    windowNumber = gtboxarray(tempIndex,2);
-    %scan rest of frames for matching window number
-    match = [];
-    for p = 2:length(filenameArr)
-        tempFrameNum = gtboxarray(sFrameArr(p),1);
-        subIndex = sFrameArr(p);
-        while(gtboxarray(subIndex,1) == tempFrameNum)
[…]

### 2015-12-11 p2/matlab/main_REMOTE_828.m

@@ -1,15 +1,0 @@
-
-clc
-%fill gtboxarray which has window information ie. max's and min's
-parseGroundTruthSupressed;
-
-numOfFrames = 3; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7022;  %starting frame; range is 7024-7200s
-filenameArr = {}; %filenames for selected frames 
-sFrameArr = [];    %starting indexes of selected frame for gtboxarray
-threshold = 40;
-alpha = 0.15;
-
-matchVals = phase1(numOfFrames, frameSkipRate, frameindex, gtboxarray, filenameArr, sFrameArr, threshold, alpha);
-

### 2015-12-11 p2/matlab/main.m
fixed merge mess up

@@ -1,5 +1,3 @@
-
-
 %fill gtboxarray which has window information ie. max's and min's
 parseGroundTruthSupressed;
 
@@ -15,85 +13,3 @@ alpha = 0.15;
 matchVals = phase1(numOfFrames, frameSkipRate, frameindex, gtboxarray, filenameArr, sFrameArr, threshold, alpha);
 
 
-%fill file name array and find the starting rows for frames in the
-%gtboxarray (this array holds all bounding box data for every window in
-%each frame
-for n = 1:numOfFrames
-    if frameindex < 7200  %make sure number of trials and skip rate doesnt exceed highest indexed frame
-        filename = strcat(filepath, num2str(frameindex));
-        
-        filename = strcat(filename, '.png');
-        %disp(filename);
-        filenameArr{end+1} = filename;
-        disp(filenameArr(n));
-        image = imread(filename);
-        
-    
-        %search for desired frames
-        r = 1;
-        while(frameindex ~= gtboxarray(r,1))
-            %disp(gtboxarray(r,1));
-            r = r + 1;
-        end
-        sFrameArr = [sFrameArr r];  %starting index of data for image in gtboxarray
-        disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
-        
-        frameindex = frameindex + frameSkipRate;
-    end
-end
-
-%run harris corner and get corners for each window
-%window is defined by column 2 in gtboxarray
-%below code identifies which windows are shared between all selected frames
-%if there is a common window then it runs harris on this window from each
-%frame
-message2 = 'running harris corners of matching windows of all frames:';
-disp(message2);
-firstFrameNum = gtboxarray(sFrameArr(1),1);
-tempIndex = sFrameArr(1);
-%disp(tempFrameNum);
-while(gtboxarray(tempIndex,1) == firstFrameNum)
-    %disp(gtboxarray(tempIndex,2));
-    windowNumber = gtboxarray(tempIndex,2);
-    %scan rest of frames for matching window number
-    match = [];
-    for p = 2:length(filenameArr)
-        tempFrameNum = gtboxarray(sFrameArr(p),1);
-        subIndex = sFrameArr(p);
-        while(gtboxarray(subIndex,1) == tempFrameNum)
-            if gtboxarray(subIndex,2) == windowNumber
-                match = [match 1];
-            end
-            subIndex = subIndex + 1;
-        end
-    end
-    %disp(match);
[…]

### 2015-12-11 p2/report/project_report.tex
initial commit for project report

\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{draftwatermark}
\usepackage {sectsty}
\usepackage{hyperref}
\usepackage [dvipsnames]{xcolor}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{purple},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  otherkeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  % numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  % stringstyle=\color{mymauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\pagestyle{fancy}
\renewcommand{\rightmark}{}

\SetWatermarkText{DRAFT}
\SetWatermarkScale{5}
\SetWatermarkLightness{.98}

\sectionfont{\color{cyan}}
\author{Sean Curran \\
\and Stephen Durofchalk \\
\and Zachary Feldman \\
\and Ryan Wails}
\title{CMPEN/EE 454 Project 2 Report}

\begin{document}

\maketitle
\thispagestyle{empty}

\newpage
\pagenumbering{roman}
\setcounter{page}{1}
\setcounter{tocdepth}{2}
\tableofcontents
\thispagestyle{plain}

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Integral Algorithms}
\subsection{Harris Corner Detection}
\subsubsection{Synopsis}
Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.  A ``corner'' can loosely be defined as a feature in the image with relatively large $\frac{\partial f}{\partial x}$ and $\frac{\partial f}{\partial y}$ values.
\subsubsection{Implementation}
Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
\begin{lstlisting}[frame=single, language=C]
// C-like psuedocode
intensity_image harris(original_image, patch_indices) {

}
\end{lstlisting}
\subsection{Patch Matching}
\subsection{RANSAC}

\end{document}

### 2015-12-11 p2/matlab/ransacWrapper.m
ransacWrapper fixes

@@ -5,24 +5,26 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
     
     w1 = windowPair;
     w2 = windowMatches{imagePair}(windowPair);
-    numPointMathes = size(cornerMatches{imagePair}{w1,w2},1);
-    for i=1:numPointMatches
-        corner1Num = i;
-        corner2Num = cornerMatches{imagePair}{w1,w2}(i);
-        if corner2Num ~= 0
-            xmin1 = gtBoxArray(sFrameArr(imagePair)+w1,3);
-            ymin1 = gtBoxArray(sFrameArr(imagePair)+w1);
-            x1 = corners{sFrameArr(imagePair)+w1}(2,corner1Num)+xmin1;
-            y1 = corners{sFrameArr(imagePair)+w1}(1,corner1Num)+ymin1;
-            data1(2,i) = x1;
-            data1(1,i) = y1;
+    if (w2 ~= 0)
+        numPointMathes = size(cornerMatches{imagePair}{w1,w2},1);
+        for i=1:numPointMatches
+            corner1Num = i;
+            corner2Num = cornerMatches{imagePair}{w1,w2}(i);
+            if corner2Num ~= 0
+                xmin1 = gtBoxArray(sFrameArr(imagePair)+w1,3);
+                ymin1 = gtBoxArray(sFrameArr(imagePair)+w1);
+                x1 = corners{sFrameArr(imagePair)+w1}(2,corner1Num)+xmin1;
+                y1 = corners{sFrameArr(imagePair)+w1}(1,corner1Num)+ymin1;
+                data1(2,i) = x1;
+                data1(1,i) = y1;
 
-            xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
-            ymin2 = gtBoxArray(sFraneArr(imagePair+1)+w2,3);
-            x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
-            y2 = corners{sFrameArr(imagePair+1)+w2}(1,corner2Num)+ymin2;
-            data2(2,i) = x2;
-            data2(1,i) = y2;
+                xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
+                ymin2 = gtBoxArray(sFraneArr(imagePair+1)+w2,3);
+                x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
[…]

### 2015-12-11 p2/report/project_report.tex
finished harris code

@@
 \lstset{ %
-  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
-  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
-  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
-  breaklines=true,                 % sets automatic line breaking
-  captionpos=b,                    % sets the caption-position to bottom
-  commentstyle=\color{purple},    % comment style
-  deletekeywords={...},            % if you want to delete keywords from the given language
-  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
-  frame=single,	                   % adds a frame around the code
-  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
-  keywordstyle=\color{blue},       % keyword style
-  language=Octave,                 % the language of the code
-  otherkeywords={*,...},            % if you want to add more keywords to the set
-  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
-  numbersep=5pt,                   % how far the line-numbers are from the code
-  % numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
-  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
-  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
-  showstringspaces=false,          % underline spaces within strings only
-  showtabs=false,                  % show tabs within strings adding particular underscores
-  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
-  % stringstyle=\color{mymauve},     % string literal style
-  tabsize=2,	                   % sets default tabsize to 2 spaces
-  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
+	language=C,
+	basicstyle=\ttfamily\footnotesize,
+	keywordstyle=\ttfamily\color{blue}\footnotesize,
+	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
+	texcl,
+	escapechar =`
+	escapebegin=\lst@commentstyle,
+	showspaces=false,
+	showtabs=false,
+	numbers=left,
+	showstringspaces=false,
+	frame=single
 }
+\makeatother
 
@@
 Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
-\begin{lstlisting}[frame=single, language=C]
-// C-like psuedocode
+\begin{lstlisting}
+
 intensity_image harris(original_image, patch_indices) {
 
+	// Compute the image patch.
+	intensity_img = convert_to_intensity_image(original_image);
+	img_patch = compute_patch(intensity_img, patch_indices);
+
+	// Compute partial x and y, mixed derivatives.
+	ix = convolve_sobel_x(img_patch);
+	iy = convolve_sobel_y(img_patch);
+
+	ix2 = ix * ix;
+	iy2 = iy * iy;
+	ixy = ix * iy;
+
+	// Compute sums using a Gaussian windowing function
+	sx2 = convolve_gaussian(ix2);
+	sy2 = convolve_gaussian(iy2);
+	sxy = convolve_gaussian(ixy);
+
+	// For each pixel in the image, compute H matrix,
+	// compute product of eigenvalues scaled by k = 0.07,
+	// and store the response value as r.
+	for (px : img_patch) {
+		H = {{sx2(px), sxy(px)}, {sxy(px) sy2(px)}};
+		r(px) = det(H) - 0.07 * trace(H) * trace(H);
 	}
+
+	return r;
+}
+
 \end{lstlisting}

### 2015-12-11 p2/matlab/ransacWrapper.m
more ransacWrapper fixes

@@ -1,27 +1,39 @@
 function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
     imagePair,windowPair,sFrameArr,gtBoxArray,corners)
     % input: image pair number and window pair number
-    % output: (x,y) coordinates for point correspondes of this window pair
+    % output: (x,y) coordinates for point correspondences of this window pair
     
+    % get the window in img1 and its corresponding window in img2
     w1 = windowPair;
     w2 = windowMatches{imagePair}(windowPair);
+    
+    % if there is a window match for the window in img1
     if (w2 ~= 0)
-        numPointMathes = size(cornerMatches{imagePair}{w1,w2},1);
+        numPointMatches = size(cornerMatches{imagePair}{w1,w2},1);
         for i=1:numPointMatches
+            % get the first corner in img1 and its corresponding corner in
+            % img2
             corner1Num = i;
             corner2Num = cornerMatches{imagePair}{w1,w2}(i);
+            % if there is a match for the corner in img1
             if corner2Num ~= 0
+                % get the top left coordinates of window 1
                 xmin1 = gtBoxArray(sFrameArr(imagePair)+w1,3);
-                ymin1 = gtBoxArray(sFrameArr(imagePair)+w1);
+                ymin1 = gtBoxArray(sFrameArr(imagePair)+w1,4);
+                % get the (x,y) coordinates of this corner
                 x1 = corners{sFrameArr(imagePair)+w1}(2,corner1Num)+xmin1;
                 y1 = corners{sFrameArr(imagePair)+w1}(1,corner1Num)+ymin1;
+                
                 data1(2,i) = x1;
                 data1(1,i) = y1;
-
+                
+                % get the top left coordinates of window 2
                 xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
-                ymin2 = gtBoxArray(sFraneArr(imagePair+1)+w2,3);
+                ymin2 = gtBoxArray(sFraneArr(imagePair+1)+w2,4);
+                % get the (x,y) coordinates of this corner
                 x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
                 y2 = corners{sFrameArr(imagePair+1)+w2}(1,corner2Num)+ymin2;
+                
                 data2(2,i) = x2;
                 data2(1,i) = y2;
             end

### 2015-12-11 p2/matlab/main.m
Working well?

@@ -1,11 +1,11 @@
 %fill gtboxarray which has window information ie. max's and min's
 parseGroundTruthSupressed;
 
-numOfFrames = 2; %set number frames 
+numOfFrames = 3; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
 frameindex = 7022;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
-threshold = 100;
+threshold = 140;
 alpha = 0.15;
 cornerPatchSizeX = 8;
 cornerPatchSizeY = 8;
@@ -13,6 +13,7 @@ cornerPatchSizeY = 8;
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);
 
+%{
 harris_img = imread('../frames/DaMultiview-seq7022.png');
 imshow(harris_img);
 
@@ -22,6 +23,7 @@ for k = 1 : numel(cs) / 2
     plot(cs(1,k), cs(2,k), 'r*');
 end
 hold off;
+%}
 
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);

### 2015-12-11 p2/matlab/ransacWrapper.m
more ransacWrapper fixes

@@ -29,13 +29,15 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 
                 % get the top left coordinates of window 2
                 xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
-                ymin2 = gtBoxArray(sFraneArr(imagePair+1)+w2,4);
+                ymin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,4);
                 % get the (x,y) coordinates of this corner
                 x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
                 y2 = corners{sFrameArr(imagePair+1)+w2}(1,corner2Num)+ymin2;
                 
                 data2(2,i) = x2;
                 data2(1,i) = y2;
+            else
+                i=i-1;
             end
         end
     end

### 2015-12-11 p2/matlab/main.m
Found a bug
the input to the hungarian algortithm for box matching contained far too
many zeros

@@ -1,14 +1,18 @@
 %fill gtboxarray which has window information ie. max's and min's
 parseGroundTruthSupressed;
 
-numOfFrames = 3; %set number frames 
+%temp = gtboxarray(1,:);
+%gtboxarray(1,:)=gtboxarray(2,:);
+%gtboxarray(2,:)=temp;
+
+numOfFrames = 2; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
 frameindex = 7022;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
-threshold = 140;
-alpha = 0.15;
-cornerPatchSizeX = 8;
-cornerPatchSizeY = 8;
+threshold = 220;
+alpha = 0.5;
+cornerPatchSizeX = 6;
+cornerPatchSizeY = 6;
 
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);

### 2015-12-11 p2/matlab/ransacWrapper.m
wrapper should work now
will test once we get correct window/corner matches in main

@@ -6,6 +6,7 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
     % get the window in img1 and its corresponding window in img2
     w1 = windowPair;
     w2 = windowMatches{imagePair}(windowPair);
+	j = 0;
     
     % if there is a window match for the window in img1
     if (w2 ~= 0)
@@ -21,11 +22,11 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 xmin1 = gtBoxArray(sFrameArr(imagePair)+w1,3);
                 ymin1 = gtBoxArray(sFrameArr(imagePair)+w1,4);
                 % get the (x,y) coordinates of this corner
-                x1 = corners{sFrameArr(imagePair)+w1}(2,corner1Num)+xmin1;
-                y1 = corners{sFrameArr(imagePair)+w1}(1,corner1Num)+ymin1;
+                x1 = corners{sFrameArr(imagePair)+w1}(2,j)+xmin1;
+                y1 = corners{sFrameArr(imagePair)+w1}(1,j)+ymin1;
                 
-                data1(2,i) = x1;
-                data1(1,i) = y1;
+                data1(2,j) = x1;
+                data1(1,j) = y1;
                 
                 % get the top left coordinates of window 2
                 xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
@@ -34,8 +35,10 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
                 y2 = corners{sFrameArr(imagePair+1)+w2}(1,corner2Num)+ymin2;
                 
-                data2(2,i) = x2;
-                data2(1,i) = y2;
+                data2(2,j) = x2;
+                data2(1,j) = y2;
+				
+				j++;
             end
         end
     end

### 2015-12-11 p2/matlab/ransacWrapper.m
wrapper working now I swear

@@ -6,7 +6,7 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
     % get the window in img1 and its corresponding window in img2
     w1 = windowPair;
     w2 = windowMatches{imagePair}(windowPair);
-	j = 0;
+	j = 1;
     
     % if there is a window match for the window in img1
     if (w2 ~= 0)

### 2015-12-11 p2/matlab/SumOfSqaureDifferences.m
fixes

@@ -1,5 +1,6 @@
 function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
-    ssd = 0;
+    %make this a long?    
+    ssd = double(0);
     t = 0;
     p1(1) = p1(1)-y/2;
     p1(2) = p1(2)-x/2;
@@ -8,15 +9,37 @@ function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
     
     dim1 = size(i1);
     dim2 = size(i2);
+    
+    w1xmin = w1(3);
+    w1ymin = w1(4);
+    w2xmin = w2(3);
+    w2ymin = w2(4);
+    
+    
+    p1x = p1(2);
+    p1y = p1(1);
+    p2x = p2(2);
+    p2y = p2(1);
+    
+    ip1x = w1xmin+p1x;
+    ip1y = w1ymin+p1y;
+    ip2x = w2xmin+p2x;
+    ip2y = w2ymin+p2y;
+    
     for i=1:x
       for j=1:y
           for k=1:3
                 %check this because there was an index out of bounds error
-                if ~(w1(4)+p1(1)+ j > dim1(1) || w1(3)+p1(2)+i > dim1(2) || ...
-                       w2(4)+p2(1)+j > dim2(1) || w2(3)+p2(2)+i > dim2(1))
-                    
-                   ssd = ssd + (i1(w1(4)+p1(1)+j,w1(3)+p1(2)+i,k)...
-                    -i2(w2(4)+p2(1)+j,w2(3)+p2(2)+i,k))^2;     
+                if ~(ip1y + j> dim1(1) || ip1x + i > dim1(2) || ...
+                       ip2y + j > dim2(1) || ip2x + i > dim2(2))
+                   
+                   pixel1 = i1(ip1y+j,ip1x+i,k);
+                   pixel2 = i2(ip2y+j,ip2x+i,k);
+                   
+                   step1 = double(pixel1)-double(pixel2);
+                   step2 = step1^2;
+                   
+                   ssd = ssd + step2;
                 end
                 
           end

### 2015-12-11 p2/matlab/matcher.m
ransac and wrapper 'done', attempted ransacDisplay

@@ -6,21 +6,21 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
     
 %match up corners
     for frame = 1:numOfFrames-1
-    frame1 = frame;
-    frame2 = frame+1;
-    frame1boxstart = sFrameArr(frame1);
-    frame2boxstart = sFrameArr(frame2);
-    %number of boxes
-    i1boxes = frame2boxstart - frame1boxstart;
-    if frame ~= numOfFrames-1
-        i2boxes = sFrameArr(frame2+1) - frame2boxstart;
-    else
-        r = frame2boxstart;
-        while(frameindex+frame == gtboxarray(r,1))
-            r = r + 1;
+        frame1 = frame;
+        frame2 = frame+1;
+        frame1boxstart = sFrameArr(frame1);
+        frame2boxstart = sFrameArr(frame2);
+        %number of boxes
+        i1boxes = frame2boxstart - frame1boxstart;
+        if frame ~= numOfFrames-1
+            i2boxes = sFrameArr(frame2+1) - frame2boxstart;
+        else
+            r = frame2boxstart;
+            while(frameindex+frame == gtboxarray(r,1))
+                r = r + 1;
+            end
+            i2boxes = r-frame2boxstart;
         end
-        i2boxes = r-frame2boxstart;
-    end
     boxmatchmatrix = zeros(i1boxes,i2boxes);
     
     filename = strcat(filepath, num2str(frameindex+frame-1));

### 2015-12-11 p2/matlab/ransac.m

@@ -1,4 +1,6 @@
-function [bestTX,bestTY] = ransac(data1,data2,iterations,thresholdDistance,inlierRatio)
+function [bestTX,bestTY,translations,translationsByWindow] = ransac(...
+    data1,data2,iterations,thresholdDistance,inlierRatio, imagePair,...
+    windowPair, translations,translationsByWindow)
 	bestTX = 0;
 	bestTY = 0;
 	bestNumInliers = 0;
@@ -34,13 +36,17 @@ function [bestTX,bestTY] = ransac(data1,data2,iterations,thresholdDistance,inlie
 			distance = sqrt((x_pred - x_real)^2 + (y_pred - y_real)^2);
 			if (distance <= thresholdDistance)
 				numInliers = numInliers+1;
-		end	
+            end
+        end
 		if (numInliers >= (inlierRatio * numDataPoints) ...
                 && numInliers > bestNumInliers)
 			bestNumInliers = numInliers;
 			bestTX = tx;
 			bestTY = ty;
 		end
-	end
+    end
+    trans = [bestTY,bestTX];
+    translationsByWindow(windowPair) = {trans};
+    translations(imagePair) = {translationsByWindow};
 end
 

### 2015-12-11 p2/matlab/ransacDisplay.m

@@ -1,0 +1,26 @@
+function [] = ransacDisplay(sFrameArr,gtboxarray,translations)
+    drawArrow = @(x,y) quiver( x(1),y(1),x(2)-x(1),y(2)-y(1),0 );
+    figure(1); clf; set(gcf,'DoubleBuffer','On');
+    j=1;
+    for fnum=7022:7023
+        fname = sprintf('../frames/DaMultiview-seq%04d.png',fnum);
+        im = imread(fname);
+        imagesc(im); axis equal
+        inds = find(gtboxarray(:,1)==fnum);
+        hold on
+        for i = 1:length(inds)
+            bb = gtboxarray(inds(i),:);
+            %plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+            %text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
+            window_x = gtboxarray(sFrameArr(j)+i-1,3);
+            window_y = gtboxarray(sFrameArr(j)+i-1,4);
+            x1 = [window_x window_x+translations{j}{i}(2)];
+            y1 = [window_y window_y+translations{j}{i}(1)];
+            drawArrow(x1,y1); hold on
+        end
+        title(sprintf('frame %d',fnum));           
+        hold off; drawnow
+        j = j+1;
+    end
+end
+

### 2015-12-11 p2/matlab/ransacWrapper.m

@@ -19,21 +19,21 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
             % if there is a match for the corner in img1
             if corner2Num ~= 0
                 % get the top left coordinates of window 1
-                xmin1 = gtBoxArray(sFrameArr(imagePair)+w1,3);
-                ymin1 = gtBoxArray(sFrameArr(imagePair)+w1,4);
+                xmin1 = gtBoxArray(sFrameArr(imagePair)+w1-1,3);
+                ymin1 = gtBoxArray(sFrameArr(imagePair)+w1-1,4);
                 % get the (x,y) coordinates of this corner
-                x1 = corners{sFrameArr(imagePair)+w1}(2,j)+xmin1;
-                y1 = corners{sFrameArr(imagePair)+w1}(1,j)+ymin1;
+                x1 = corners{sFrameArr(imagePair)+w1-1}(2,j)+xmin1;
+                y1 = corners{sFrameArr(imagePair)+w1-1}(1,j)+ymin1;
                 
                 data1(2,j) = x1;
                 data1(1,j) = y1;
                 
                 % get the top left coordinates of window 2
-                xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,3);
-                ymin2 = gtBoxArray(sFrameArr(imagePair+1)+w2,4);
+                xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2-1,3);
+                ymin2 = gtBoxArray(sFrameArr(imagePair+1)+w2-1,4);
                 % get the (x,y) coordinates of this corner
-                x2 = corners{sFrameArr(imagePair+1)+w2}(2,corner2Num)+xmin2;
-                y2 = corners{sFrameArr(imagePair+1)+w2}(1,corner2Num)+ymin2;
+                x2 = corners{sFrameArr(imagePair+1)+w2-1}(2,corner2Num)+xmin2;
+                y2 = corners{sFrameArr(imagePair+1)+w2-1}(1,corner2Num)+ymin2;
                 
                 data2(2,j) = x2;
                 data2(1,j) = y2;

### 2015-12-11 p2/matlab/SumOfSqaureDifferences.m
5/7 biotch

@@ -1,5 +1,8 @@
 function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
     %make this a long?    
+    
+
+    
     ssd = double(0);
     t = 0;
     p1(1) = p1(1)-y/2;
@@ -28,7 +31,7 @@ function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
     
     for i=1:x
       for j=1:y
-          for k=1:3
+          for k=1
                 %check this because there was an index out of bounds error
                 if ~(ip1y + j> dim1(1) || ip1x + i > dim1(2) || ...
                        ip2y + j > dim2(1) || ip2x + i > dim2(2))

### 2015-12-11 p2/matlab/blob2px.m

@@ -34,8 +34,8 @@ for i = 1 : rows
     for j = 1 : cols
         if (bw_img(i,j) == 1)
             px = zeros(2,1);
-            px(1,1) = j;
-            px(2,1) = i;
+            px(1,1) = i;
+            px(2,1) = j;
             output_args = [output_args px];
         end
     end

### 2015-12-11 p2/matlab/main.m

@@ -9,10 +9,10 @@ numOfFrames = 2; %set number frames
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
 frameindex = 7022;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
-threshold = 220;
-alpha = 0.5;
-cornerPatchSizeX = 6;
-cornerPatchSizeY = 6;
+threshold = 230;
+alpha = 0.15;
+cornerPatchSizeX = 20;
+cornerPatchSizeY = 20;
 
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);

### 2015-12-11 p2/matlab/matcher.m

@@ -30,6 +30,9 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
     filename = strcat(filename, '.png');
     i2 = imread(filename);
     
+    i1 = rgb2gray(i1);
+    i2 = rgb2gray(i2);
+    
     %cornerMatchesByWindow;% = [];%zeros(i1boxes,i2boxes);
     
         for b1 = 1:i1boxes
@@ -44,6 +47,39 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
                 i2corners = dim2(2);
        
                 cornermatchmatrix = zeros(i1corners,i2corners);
+                
+                   %{
+                    figure;
+                    imagesc(i1);
+
+                    hold on
+                    cs = corners{frame1boxstart+b1-1}(:,:);
+                    cs(1,:) = cs(1,:)+w1(4);
+                    cs(2,:) = cs(2,:)+w1(3);
+                    cs1 = cs;
+                    bb = w1;
+                    for k = 1 : numel(cs) / 2
+                        plot(cs(2,k), cs(1,k), 'r*');
+                        plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+                    end
+                    hold off;
+                    
+                    figure;
+                    imagesc(i1);
+
+                    hold on
+                    cs = corners{frame2boxstart+b2-1}(:,:);
+                    bb = w2;
+                    cs(1,:) = cs(1,:)+w2(4);
+                    cs(2,:) = cs(2,:)+w2(3);
+                    cs2 = cs;
+                    for k = 1 : numel(cs) / 2
+                        plot(cs(2,k), cs(1,k), 'r*');
+                        plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+                    end
+                    hold off;
+                   %}
+                
                 for c1 = 1:i1corners
                    for c2 = 1:i2corners
                         ssd = SumOfSqaureDifferences(...

### 2015-12-11 p2/matlab/main.m
4/7 on 5 frames

@@ -5,14 +5,14 @@ parseGroundTruthSupressed;
 %gtboxarray(1,:)=gtboxarray(2,:);
 %gtboxarray(2,:)=temp;
 
-numOfFrames = 2; %set number frames 
+numOfFrames = 5; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
 frameindex = 7022;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
-threshold = 230;
+threshold = 235;
 alpha = 0.15;
-cornerPatchSizeX = 20;
-cornerPatchSizeY = 20;
+cornerPatchSizeX = 16;
+cornerPatchSizeY = 16;
 
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);

### 2015-12-11 p2/matlab/main.m
worked really well on 10 frames

@@ -5,14 +5,14 @@ parseGroundTruthSupressed;
 %gtboxarray(1,:)=gtboxarray(2,:);
 %gtboxarray(2,:)=temp;
 
-numOfFrames = 5; %set number frames 
+numOfFrames = 10; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
 frameindex = 7022;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
 threshold = 235;
 alpha = 0.15;
-cornerPatchSizeX = 16;
-cornerPatchSizeY = 16;
+cornerPatchSizeX = 12;
+cornerPatchSizeY = 12;
 
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);

### 2015-12-11 p2/matlab/ncc.m
NCC function

@@ -1,0 +1,15 @@
+function [ ncc ] = ncc( p1,p2,x,y )
+    ncc1 = 0;
+    ncc2 = 0;
+    ncc3 = 0;
+    ncc = 0;
+    
+    for i=1:x
+      for j=1:y
+        ncc1 = ncc1 + (p1(i,j)*p2(i,j));
+        ncc2 = ncc2 + (p1(i,j) * p1(i,j));
+        ncc3 = ncc3 + (p2(i,j) * p2(i,j));
+        ncc = ncc + ncc1/sqrt(ncc2 * ncc3);
+      end
+    end
+end

### 2015-12-11 p2/matlab/main.m
78% accuracy

@@ -33,4 +33,18 @@ hold off;
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
 
-    
+count = 0;
+count2 = 0;
+for i=1:9
+    dims = size(windowMatches{i});
+    for j=1:dims(1)
+       if windowMatches{i}(j) == j
+           count = count + 1;
+       end
+       count2 = count2+1;
+    end
+end
+
+display(count);
+display(count2);
+display(double(count)/double(count2));

### 2015-12-11 p2/matlab/matcher.m

@@ -97,10 +97,54 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
         end
         cornerMatches(frame) = {cornerMatchesByWindow};
         
+        
+        
         [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
+        
+        for abox=1:numel(aboxes)
+        
+            w1 = gtboxarray(frame1boxstart+abox-1,:);
+            w2 = gtboxarray(frame2boxstart+aboxes(abox)-1,:);
+                
+            figure;
+            imagesc(i1);
+
+            hold on
+            cs = corners{frame1boxstart+b1-1}(:,:);
+            cs(1,:) = cs(1,:)+w1(4);
+            cs(2,:) = cs(2,:)+w1(3);
+            cs1 = cs;
+            bb = w1;
+            for k = 1 : numel(cs) / 2
+                plot(cs(2,k), cs(1,k), 'r*');
+                plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+            end
+            hold off;
+
+            figure;
+            imagesc(i2);
+
+            hold on
+            cs = corners{frame2boxstart+b2-1}(:,:);
+            bb = w2;
+            cs(1,:) = cs(1,:)+w2(4);
+            cs(2,:) = cs(2,:)+w2(3);
+            cs2 = cs;
+            for k = 1 : numel(cs) / 2
+                plot(cs(2,k), cs(1,k), 'r*');
+                plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+            end
+            hold off;
+            
+            close all force;
+            
+                    
+        end
+        
         windowMatches(frame) = {aboxes};
     end
 
+  
 
 end
 

### 2015-12-11 p2/matlab/matcher.m
dumb commit

@@ -101,6 +101,7 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
         
         [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
         
+        %{
         for abox=1:numel(aboxes)
         
             w1 = gtboxarray(frame1boxstart+abox-1,:);
@@ -140,6 +141,7 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
             
                     
         end
+        %}
         
         windowMatches(frame) = {aboxes};
     end

### 2015-12-11 p2/report/project_report.tex
added image for after phase 1, started patch matching section

@@
 \usepackage{hyperref}
+\usepackage{graphicx}
+\graphicspath{ {img/} }
 \usepackage [dvipsnames]{xcolor}
@@
 Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.
-A ``corner'' can loosely be defined as a feature in the image with relatively large $\frac{\partial f}{\partial x}$ and $\frac{\partial f}{\partial y}$ values.
+A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial f}{\partial x}(x_0,y_0)$ and $\frac{\partial f}{\partial y}(x_0,y_0)$ yield relatively large values.
 \subsubsection{Implementation}
@@
 \end{lstlisting}
+This routine returns a non-normalized intensity image where strong intensities correspond to corner points in the image patch.
+Once this intensity image has been computed, it is passed to a thresholding routine where the coordinate points of these corners is determined.
+
+\newpage
+\begin{lstlisting}
+
+pixel_array compute_coordinates(intensity_image, threshold) {
+
+	// First, we optionally use a monte-carlo pruning algorithm
+	// to reduce the number of corner coordinated produced by this
+	// function.
+	prune(intensity_image);
+
+	// Next, the intensity image is converted to a binary image.
+	b_img = threshold_to_binary(intensity_image, threshold);
+
+	// Finally, any pixel with a value of 1 in the binary image
+	// is considered a corner point coordinate.
+	for (px : b_img) {
+		p_arr += px;
+	}
+
+	return p_arr;
+}
+
+\end{lstlisting}
+
+\newpage
 \subsection{Patch Matching}
+\subsubsection{Synopsis}
+After the corner point coordinates of each image has been computed, the bounding boxes for each image and corresponding corner points are passed to a patch matching routine.
+This patch matching routine computes correspondences between corner points and between bounding boxes (explained in more detail below).
+The in the system pictured below, assuming the image in bounding boxes 1 and 3 are similar and the images in bounding boxes 2 and 4 are similar, the output for this phase would be:
+\\~\\
+$(1 \iff 3, \text{assignment cost})$
+\\
+$(2 \iff 4, \text{assignment cost})$
+\\~\\
+\includegraphics[width=\textwidth]{after_corner}
+
 \subsection{RANSAC}

### 2015-12-12 p2/matlab/ncc.m
dumb commit (because of ryan)

@@ -1,4 +1,31 @@
-function [ ncc ] = ncc( p1,p2,x,y )
+function [ ncc ] = ncc( p1,p2,pp1,pp2,x,y,w1,w2 )
+    
+    
+    pp1(1) = pp1(1)-y/2;
+    pp1(2) = pp1(2)-x/2;
+    pp2(1) = pp2(1)-y/2;
+    pp2(2) = pp2(2)-x/2;
+    
+    dim1 = size(p1);
+    dim2 = size(p2);
+    
+    w1xmin = w1(3);
+    w1ymin = w1(4);
+    w2xmin = w2(3);
+    w2ymin = w2(4);
+    
+    
+    p1x = pp1(2);
+    p1y = pp1(1);
+    p2x = pp2(2);
+    p2y = pp2(1);
+    
+    ip1x = w1xmin+p1x;
+    ip1y = w1ymin+p1y;
+    ip2x = w2xmin+p2x;
+    ip2y = w2ymin+p2y;
+
+
     ncc1 = 0;
     ncc2 = 0;
     ncc3 = 0;
@@ -6,9 +33,9 @@ function [ ncc ] = ncc( p1,p2,x,y )
     
     for i=1:x
       for j=1:y
-        ncc1 = ncc1 + (p1(i,j)*p2(i,j));
-        ncc2 = ncc2 + (p1(i,j) * p1(i,j));
-        ncc3 = ncc3 + (p2(i,j) * p2(i,j));
+        ncc1 = ncc1 + (p1(ip1y+i,ip1x+j)*p2(ip2y+i,ip2x+j));
+        ncc2 = ncc2 + (p1(ip1y+i,ip1x+j) * p1(ip1y+i,ip1x+j));
+        ncc3 = ncc3 + (p2(ip2y+i,ip2x+j) * p2(ip2y+i,ip2x+j));
         ncc = ncc + ncc1/sqrt(ncc2 * ncc3);
       end
     end

### 2015-12-12 p2/matlab/main.m
updated main with ransac

@@ -32,5 +32,16 @@ hold off;
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
-
+translations={};
+translationsByWindow = {};
+groundTruthTranslations;
+for i=1:size(cornerMatches,2)
+    disp(['running ransac on image: ',num2str(i)]);
+    for j=1:size(windowMatches{i},1)
+        [data1,data2] = ransacWrapper(cornerMatches,windowMatches,i,j,...
+            sFrameArr,gtboxarray,corners);
+        [translations,translationsByWindow] = ransac(data1,data2,10000,1,...
+            0.1,i,j,translations,translationsByWindow);
+    end
+end
     

### 2015-12-12 p2/matlab/ransac.m

@@ -1,4 +1,4 @@
-function [bestTX,bestTY,translations,translationsByWindow] = ransac(...
+function [translations,translationsByWindow] = ransac(...
     data1,data2,iterations,thresholdDistance,inlierRatio, imagePair,...
     windowPair, translations,translationsByWindow)
 	bestTX = 0;

### 2015-12-12 p2/matlab/ransacDisplay.m

@@ -2,7 +2,7 @@ function [] = ransacDisplay(sFrameArr,gtboxarray,translations)
     drawArrow = @(x,y) quiver( x(1),y(1),x(2)-x(1),y(2)-y(1),0 );
     figure(1); clf; set(gcf,'DoubleBuffer','On');
     j=1;
-    for fnum=7022:7023
+    for fnum=7022:7030
         fname = sprintf('../frames/DaMultiview-seq%04d.png',fnum);
         im = imread(fname);
         imagesc(im); axis equal

### 2015-12-12 p2/matlab/Acurrator.m
commit to merge with master

@@ -1,0 +1,3 @@
+function [accuracy] = Accurator(windowMathces, gtboxarray, sFrameArr)
+    
+end

### 2015-12-12 p2/matlab/Acurrator.m
accurator done and tested

@@ -1,3 +1,16 @@
-function [accuracy] = Accurator(windowMathces, gtboxarray, sFrameArr)
-    
+function [accuracy] = Acurrator(windowMatches, gtboxarray, sFrameArr)
+    correct = 0;
+    total = 0;
+    dims = size(sFrameArr);
+    for i=1:dims(2)-1
+        dimwindows = size(windowMatches{i});
+        for j = 1:dimwindows(1)
+            if gtboxarray(sFrameArr(i+1) + windowMatches{i}(j) - 1,2)...
+                  == gtboxarray(sFrameArr(i) + j - 1,2)
+               correct = correct + 1;
+            end
+            total = total + 1;
+        end
+    end
+    accuracy = double(correct)/double(total);
 end

### 2015-12-12 p2/matlab/main.m

@@ -13,7 +13,7 @@ threshold = 235;
 alpha = 0.15;
 cornerPatchSizeX = 12;
 cornerPatchSizeY = 12;
-
+%get boxes and features (harris corners)
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);
 
@@ -28,12 +28,12 @@ for k = 1 : numel(cs) / 2
 end
 hold off;
 %}
-
+%match
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
 
-
+%Compute Accuracy
 count = 0;
 count2 = 0;
 for i=1:9
@@ -50,6 +50,8 @@ display(count);
 display(count2);
 display(double(count)/double(count2));
 
+display(Acurrator(windowMatches,gtboxarray,sFrameArr));
+%Ransac
 translations={};
 translationsByWindow = {};
 groundTruthTranslations;

### 2015-12-12 p2/matlab/ransacDisplay.m
ransacDisplay almost done

@@ -1,26 +1,29 @@
-function [] = ransacDisplay(sFrameArr,gtboxarray,translations)
-    drawArrow = @(x,y) quiver( x(1),y(1),x(2)-x(1),y(2)-y(1),0 );
+function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
+    sFrameArr,gtboxarray,corners,translations)
     figure(1); clf; set(gcf,'DoubleBuffer','On');
-    j=1;
-    for fnum=7022:7030
-        fname = sprintf('../frames/DaMultiview-seq%04d.png',fnum);
-        im = imread(fname);
-        imagesc(im); axis equal
-        inds = find(gtboxarray(:,1)==fnum);
-        hold on
-        for i = 1:length(inds)
-            bb = gtboxarray(inds(i),:);
-            %plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
-            %text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
-            window_x = gtboxarray(sFrameArr(j)+i-1,3);
-            window_y = gtboxarray(sFrameArr(j)+i-1,4);
-            x1 = [window_x window_x+translations{j}{i}(2)];
-            y1 = [window_y window_y+translations{j}{i}(1)];
-            drawArrow(x1,y1); hold on
+    fnum = gtboxarray(sFrameArr(imagePair+1),1);
+    fname = sprintf('../frames/DaMultiview-seq%04d.png',fnum);
+    im = imread(fname);
+    imagesc(im); axis equal
+    hold on
+    for i = 1:size(windowMatches{imagePair}(1))
+        [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
+            imagePair,i,sFrameArr,gtboxarray,corners);
+        bb = gtboxarray(inds(i),:);
+        plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+        text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
+        numDataPoints = size(data1,2);
+        for j = 1:numDataPoints
+            x_real = data2(2,j);
+            y_real = data2(1,j);
+            x_pred = data1(2,j)+translations{imagePair}{j}(2);
+            y_pred = data1(1,j)+translations{imagePair}{j}(1);
+            plot(x_real,y_real,'g*');
+            plot(x_pred,y_pred,'r*');
[…]

### 2015-12-12 p2/matlab/main.m
masher can start at any image index, aka the 7170 bug is fixed. Also it got 97% accuracy!

@@ -7,7 +7,7 @@ parseGroundTruthSupressed;
 
 numOfFrames = 10; %set number frames 
 frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7022;  %starting frame; range is 7024-7200s
+frameindex = 7170;  %starting frame; range is 7024-7200s
 filepath = '../frames/DaMultiview-seq';
 threshold = 235;
 alpha = 0.15;

### 2015-12-12 p2/matlab/matcher.m

@@ -10,6 +10,8 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
         frame2 = frame+1;
         frame1boxstart = sFrameArr(frame1);
         frame2boxstart = sFrameArr(frame2);
+        frame1boxstartcorners = frame1boxstart - sFrameArr(frame1) + 1;
+        frame2boxstartcorners = frame2boxstart - sFrameArr(frame2) + 1;
         %number of boxes
         i1boxes = frame2boxstart - frame1boxstart;
         if frame ~= numOfFrames-1
@@ -41,8 +43,8 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
                 w1 = gtboxarray(frame1boxstart+b1-1,:);
                 w2 = gtboxarray(frame2boxstart+b2-1,:);
                 %number of corners
-                dim1 = size(corners{frame1boxstart+b1-1});
-                dim2 = size(corners{frame2boxstart+b2-1});
+                dim1 = size(corners{frame1boxstartcorners+b1-1});
+                dim2 = size(corners{frame2boxstartcorners+b2-1});
                 i1corners = dim1(2);
                 i2corners = dim2(2);
        
@@ -83,8 +85,8 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
                 for c1 = 1:i1corners
                    for c2 = 1:i2corners
                         ssd = SumOfSqaureDifferences(...
-                            i1,i2,corners{frame1boxstart+b1-1}(:,c1),...
-                            corners{frame2boxstart+b2-1}(:,c2),cornerpatchx,...
+                            i1,i2,corners{frame1boxstartcorners+b1-1}(:,c1),...
+                            corners{frame2boxstartcorners+b2-1}(:,c2),cornerpatchx,...
                             cornerpatchy,w1,w2);
                         cornermatchmatrix(c1,c2) = ssd;
                    end

### 2015-12-12 p2/report/project_report.tex
added section for implementation
added code for cost function

@@
 
-\newpage
+\begin{minipage}{\textwidth}
 \begin{lstlisting}
@@
 \end{lstlisting}
+\end{minipage}
 
@@
 This patch matching routine computes correspondences between corner points and between bounding boxes (explained in more detail below).
-The in the system pictured below, assuming the image in bounding boxes 1 and 3 are similar and the images in bounding boxes 2 and 4 are similar, the output for this phase would be:
-\\~\\
-$(1 \iff 3, \text{assignment cost})$
+The in the system pictured below, assuming the image in bounding boxes 1 and 3 are similar and the images in bounding boxes 2 and 4 are similar, the correspondence set output for this phase would be:
+\[
+\left \{
+\begin{tabular}{c}
+$(1 \iff 3,\quad \text{assignment cost})$ \\
+$(2 \iff 4,\quad \text{assignment cost})$
+\end{tabular}
+\right \}
+\]
+\includegraphics[width=\textwidth]{after_corner}
+\subsubsection{Implementation}
+To find an optimal bounding box correspondence set between two images, we first must compute cost values for matching two boxes.  Here is the implemented cost function:
 \\
-$(2 \iff 4, \text{assignment cost})$
-\\~\\
-\includegraphics[width=\textwidth]{after_corner}
+\begin{minipage}{\textwidth}
+\begin{lstlisting}
 
+assignment_set compute_cost(bounding_box a,b) {
+
+	// Compute the costs of corresponding each corner
+	// point in bounding box a against every corner
+	// point in bounding box b.
+	for (corner c_a : a) {
+	for (corner c_b : b) {
+		// Get the image patches around each corner point.
+		patch_a = get_patch(c_a);
+		patch_b = get_patch(c_b);
+
+		// Use SSD as cost function.
+		cost_matrix[i, j] =
+			sum_squared_difference(patch_a, patch_b);
+	} }
+
+	// Use the provided optimal assingment algorithm to get
+	// a point correspondence set and the costs assiociated
+	// with each assignment.
+	return assignmentoptimal(cost_matrix);
+}
+
+\end{lstlisting}
+\end{minipage}
 \subsection{RANSAC}

### 2015-12-12 p2/matlab/main.m
main updates

@@ -1,57 +1,35 @@
+%Parameters
+numOfFrames = 10; %set number frames 
+frameSkipRate = 1; %frame comparison distance
+frameindex = 7170;  %starting frame; range is 7022-7200
+filepath = '../frames/DaMultiview-seq';
+threshold = 235; %R threshold for harris corners
+alpha = 255; %controls how you want to choose corners at random
+                %small alpha makes corners with larger R's more 
+                %likely to be selected
+                %255 turns the "probability weighting" feature off
+%size of the patches to use around corners when matching
+cornerPatchSizeX = 12;
+cornerPatchSizeY = 12;
+
 %fill gtboxarray which has window information ie. max's and min's
 parseGroundTruthSupressed;
 
-%temp = gtboxarray(1,:);
-%gtboxarray(1,:)=gtboxarray(2,:);
-%gtboxarray(2,:)=temp;
-
-numOfFrames = 10; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7170;  %starting frame; range is 7024-7200s
-filepath = '../frames/DaMultiview-seq';
-threshold = 235;
-alpha = 0.15;
-cornerPatchSizeX = 12;
-cornerPatchSizeY = 12;
 %get boxes and features (harris corners)
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);
 
-%{
-harris_img = imread('../frames/DaMultiview-seq7022.png');
-imshow(harris_img);
-
-hold on
-cs = corners{7};
-for k = 1 : numel(cs) / 2
-    plot(cs(1,k), cs(2,k), 'r*');
-end
-hold off;
-%}
-%match
+%match corners and match boxes
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
-
 %Compute Accuracy
-count = 0;
-count2 = 0;
-for i=1:9
-    dims = size(windowMatches{i});
-    for j=1:dims(1)
-       if windowMatches{i}(j) == j
-           count = count + 1;
-       end
-       count2 = count2+1;
-    end
-end
+accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);
+disp( sprintf( ...
[…]

### 2015-12-12 p2/matlab/phase1.m
fixed indexing problem, it was causing it to say there were more corners than there were in the corner match output

@@ -12,7 +12,7 @@ function [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate,...
             filename = strcat(filename, '.png');
             %disp(filename);
             filenameArr{end+1} = filename;
-            disp(filenameArr(n));
+            %disp(filenameArr(n));
 
             %search for desired frames
             r = 1;
@@ -21,7 +21,7 @@ function [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate,...
                 r = r + 1;
             end
             sFrameArr = [sFrameArr r];  %starting index of data for image in gtboxarray
-            disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
+            %disp(['starting row in gtboxarray for above frame: ', num2str(sFrameArr(n))]);
 
             frameindex = frameindex + frameSkipRate;
         end

### 2015-12-12 p2/matlab/main.m
dumb commit

@@ -1,68 +1,0 @@
-%fill gtboxarray which has window information ie. max's and min's
-parseGroundTruthSupressed;
-
-%temp = gtboxarray(1,:);
-%gtboxarray(1,:)=gtboxarray(2,:);
-%gtboxarray(2,:)=temp;
-
-numOfFrames = 10; %set number frames 
-frameSkipRate = 1; %distance between next frame chosen, greater the distance more of a change of windows
-frameindex = 7170;  %starting frame; range is 7024-7200s
-filepath = '../frames/DaMultiview-seq';
-threshold = 235;
-alpha = 0.15;
-cornerPatchSizeX = 12;
-cornerPatchSizeY = 12;
-%get boxes and features (harris corners)
-[corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
-    gtboxarray, filepath, threshold, alpha);
-
-%{
-harris_img = imread('../frames/DaMultiview-seq7022.png');
-imshow(harris_img);
-
-hold on
-cs = corners{7};
-for k = 1 : numel(cs) / 2
-    plot(cs(1,k), cs(2,k), 'r*');
-end
-hold off;
-%}
-%match
-[cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
-    gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
-
-
-%Compute Accuracy
-count = 0;
-count2 = 0;
-for i=1:9
-    dims = size(windowMatches{i});
-    for j=1:dims(1)
-       if windowMatches{i}(j) == j
-           count = count + 1;
-       end
-       count2 = count2+1;
-    end
-end
-
-display(count);
-display(count2);
-display(double(count)/double(count2));
-
-display(Acurrator(windowMatches,gtboxarray,sFrameArr));
-%Ransac
-translations={};
-translationsByWindow = {};
-groundTruthTranslations;
-for i=1:size(cornerMatches,2)
-    disp(['running ransac on image: ',num2str(i)]);
-    for j=1:size(windowMatches{i},1)
-        [data1,data2] = ransacWrapper(cornerMatches,windowMatches,i,j,...
-            sFrameArr,gtboxarray,corners);
-        [translations,translationsByWindow] = ransac(data1,data2,10000,1,...
-            0.1,i,j,translations,translationsByWindow);
-    end
-end
-    
-

### 2015-12-12 p2/matlab/ransacDisplay.m
dumb commit

@@ -3,6 +3,7 @@ function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
     figure(1); clf; set(gcf,'DoubleBuffer','On');
     fnum = gtboxarray(sFrameArr(imagePair+1),1);
     fname = sprintf('../frames/DaMultiview-seq%04d.png',fnum);
+    inds = find(gtboxarray(:,1)==fnum);
     im = imread(fname);
     imagesc(im); axis equal
     hold on

### 2015-12-12 p2/matlab/ransacWrapper.m

@@ -22,8 +22,8 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 xmin1 = gtBoxArray(sFrameArr(imagePair)+w1-1,3);
                 ymin1 = gtBoxArray(sFrameArr(imagePair)+w1-1,4);
                 % get the (x,y) coordinates of this corner
-                x1 = corners{sFrameArr(imagePair)+w1-1}(2,j)+xmin1;
-                y1 = corners{sFrameArr(imagePair)+w1-1}(1,j)+ymin1;
+                x1 = corners{sFrameArr(imagePair)+w1-sFrameArr(1)}(2,j)+xmin1;
+                y1 = corners{sFrameArr(imagePair)+w1-sFrameArr(1)}(1,j)+ymin1;
                 
                 data1(2,j) = x1;
                 data1(1,j) = y1;
@@ -32,8 +32,9 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 xmin2 = gtBoxArray(sFrameArr(imagePair+1)+w2-1,3);
                 ymin2 = gtBoxArray(sFrameArr(imagePair+1)+w2-1,4);
                 % get the (x,y) coordinates of this corner
-                x2 = corners{sFrameArr(imagePair+1)+w2-1}(2,corner2Num)+xmin2;
-                y2 = corners{sFrameArr(imagePair+1)+w2-1}(1,corner2Num)+ymin2;
+                x2 = corners{sFrameArr(imagePair+1)+w2-sFrameArr(1)}(2,corner2Num)+xmin2;
+
+                y2 = corners{sFrameArr(imagePair+1)+w2-sFrameArr(1)}(1,corner2Num)+ymin2;
                 
                 data2(2,j) = x2;
                 data2(1,j) = y2;

### 2015-12-12 p2/report/project_report.tex
maybe done with matching?

@@
 Harris corner detection is an algorithm which detect corners in images that can be used to create point correspondences between time series images.
-A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial f}{\partial x}(x_0,y_0)$ and $\frac{\partial f}{\partial y}(x_0,y_0)$ yield relatively large values.
+A ``corner'' can loosely be defined as a feature in the image located at coordinates $(x_0,y_0)$ such that $\frac{\partial I}{\partial x}(x_0,y_0)$ and $\frac{\partial I}{\partial y}(x_0,y_0)$ yield relatively large values.
 \subsubsection{Implementation}
@@
 	// is considered a corner point coordinate.
+	// 
+	// The notation for(x:y) is used to mean "for each element x
+	// in the set y."
 	for (px : b_img) {
-		p_arr += px;
+		p_array.add(px);
 	}
 
-	return p_arr;
+	return p_array;
 }
@@
 
-assignment_set compute_cost(bounding_box a,b) {
+assignment_set compute_bb_set(bounding_box a,b) {
 
@@
 	// point in bounding box b.
-	for (corner c_a : a) {
-	for (corner c_b : b) {
+	for (corner_a : a) {
+	for (corner_b : b) {
 		// Get the image patches around each corner point.
-		patch_a = get_patch(c_a);
-		patch_b = get_patch(c_b);
+		patch_a = get_patch(corner_a);
+		patch_b = get_patch(corner_b);
 
 		// Use SSD as cost function.
-		cost_matrix[i, j] =
+		cost_matrix[corner_a, corner_b] =
 			sum_squared_difference(patch_a, patch_b);
@@
 \end{minipage}
+\\~\\
+For the bounding boxes pictured below, here is an example assignment set:
+\[
+\left \{
+\begin{tabular}{c}
+$(G \iff J,\quad \text{SSD}_{GJ})$ \\
+$(F \iff K,\quad \text{SSD}_{FK})$ \\
+$(I \iff M,\quad \text{SSD}_{IM})$ \\
+$(E \iff \emptyset,\quad \infty)$ \\
+$(H \iff \emptyset,\quad \infty)$
+\end{tabular}
+\right \}
+\]
+The overall cost of assigning Bounding Box 1 to Bounding Box 2 is then the sum of the finite costs in the optimal assignment set; i.e. $\text{SSD}_{GJ} + \text{SSD}_{FK} + \text{SSD}_{IM}$.
+\begin{center}
+\fbox{\includegraphics[width=0.65\textwidth]{box_corners}}
+\end{center}
+~\\
+A similar method is used to find an optimal bounding box correspondence between two images:
+\\
+\begin{minipage}{\textwidth}
+\begin{lstlisting}
+
+assignment_set compute_img_set(image a,b) {
+
+	// Compute the costs of corresponding each bounding box
+	// in image a against every bounding box in image b.
+	for (bounding_box_a : a) {
+	for (bounding_box_b : b) {
+
+		bb_set =
+		compute_bb_set(bounding_box_a, bounding_box_b);
+
+		// Sum the costs for the valid assignments
+		total_cost = 0;
+		for (assignment : bb_set) 
+			if (assignment.cost < inf)
+				total_cost += assignment.cost;
+
+		cost_matrix[bounding_box_a, bounding_box_b] =
+			total_cost;
+
+	} }
+
+	return assignmentoptimal(cost_matrix);
+}
+
+\end{lstlisting}
+\end{minipage}
 \subsection{RANSAC}

### 2015-12-12 p2/matlab/main.m
Read Bug, Ransac Bug, Pics
Removed bugs in reading bounding boxes, removed ransac bugs, added in
pictures to demonstrate ransac results.

@@ -1,7 +1,7 @@
 %Parameters
-numOfFrames = 10; %set number frames 
+numOfFrames = 20; %set number frames 
 frameSkipRate = 1; %frame comparison distance
-frameindex = 7170;  %starting frame; range is 7022-7200
+frameindex = 7022;  %starting frame; range is 7022-7200
 filepath = '../frames/DaMultiview-seq';
 threshold = 235; %R threshold for harris corners
 alpha = 255; %controls how you want to choose corners at random

### 2015-12-12 p2/matlab/ransacDisplay.m

@@ -7,7 +7,7 @@ function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
     im = imread(fname);
     imagesc(im); axis equal
     hold on
-    for i = 1:size(windowMatches{imagePair}(1))
+    for i = 1:size(windowMatches{imagePair})
         [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
             imagePair,i,sFrameArr,gtboxarray,corners);
         bb = gtboxarray(inds(i),:);
@@ -17,14 +17,13 @@ function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
         for j = 1:numDataPoints
             x_real = data2(2,j);
             y_real = data2(1,j);
-            x_pred = data1(2,j)+translations{imagePair}{j}(2);
-            y_pred = data1(1,j)+translations{imagePair}{j}(1);
+            x_pred = data1(2,j)+translations{imagePair}{1}(2);
+            y_pred = data1(1,j)+translations{imagePair}{1}(1);
             plot(x_real,y_real,'g*');
             plot(x_pred,y_pred,'r*');
         end
     end
     title(sprintf('frame %d',fnum));           
     hold off; drawnow
-    j = j+1;
 end
 

### 2015-12-12 p2/matlab/ransacWrapper.m

@@ -40,6 +40,8 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
                 data2(1,j) = y2;
 				
 				j = j+1;
+            else
+                numPointMatches = numPointMatches - 1;
             end
         end
     end

### 2015-12-12 p2/matlab/main.m
fixed ransac and wrapper bugs, and ssd bug

@@ -1,5 +1,5 @@
 %Parameters
-numOfFrames = 20; %set number frames 
+numOfFrames = 30; %set number frames 
 frameSkipRate = 1; %frame comparison distance
 frameindex = 7022;  %starting frame; range is 7022-7200
 filepath = '../frames/DaMultiview-seq';

### 2015-12-12 p2/matlab/ransac.m

@@ -5,45 +5,47 @@ function [translations,translationsByWindow] = ransac(...
 	bestTY = 0;
 	bestNumInliers = 0;
 	numDataPoints = size(data1, 2);
-	for i=1:iterations
-		numInliers = 0;
-		% grab 1 random pair of matching points
-        % random number between 1 and numDataPoints
-		randIndex = randi([1 numDataPoints],1,1);	
-		randDataPoint1 = data1(:,randIndex);
-		randDataPoint2 = data2(:,randIndex);
-		
-		% (x1,y1) is the point in the first region
-		% (x2,y2) is its matching point in the second region
-		x1 = randDataPoint1(2,1);
-		y1 = randDataPoint1(1,1);
-		x2 = randDataPoint2(2,1);
-		y2 = randDataPoint2(1,1);
-		
-		% translation between the 2 points
-		tx = x2-x1;
-		ty = y2-y1;
-		
-		% loop through all data points
-		for j=1:numDataPoints
-			x_pred = data1(2,j) + tx;
-			y_pred = data1(1,j) + ty;
-			x_real = data2(2,j);
-			y_real = data2(1,j);
-			
-			% calculate distance from the predicted location ...
-            % of this point to its actual location
-			distance = sqrt((x_pred - x_real)^2 + (y_pred - y_real)^2);
-			if (distance <= thresholdDistance)
-				numInliers = numInliers+1;
+    if numDataPoints ~= 0
+        for i=1:iterations
+            numInliers = 0;
+            % grab 1 random pair of matching points
+            % random number between 1 and numDataPoints
+            randIndex = randi([1 numDataPoints],1,1);	
+            randDataPoint1 = data1(:,randIndex);
+            randDataPoint2 = data2(:,randIndex);
+
+            % (x1,y1) is the point in the first region
+            % (x2,y2) is its matching point in the second region
+            x1 = randDataPoint1(2,1);
+            y1 = randDataPoint1(1,1);
+            x2 = randDataPoint2(2,1);
+            y2 = randDataPoint2(1,1);
+
+            % translation between the 2 points
+            tx = x2-x1;
+            ty = y2-y1;
+
+            % loop through all data points
+            for j=1:numDataPoints
+                x_pred = data1(2,j) + tx;
+                y_pred = data1(1,j) + ty;
+                x_real = data2(2,j);
+                y_real = data2(1,j);
+
+                % calculate distance from the predicted location ...
+                % of this point to its actual location
[…]

### 2015-12-12 p2/matlab/ransacWrapper.m

@@ -2,7 +2,8 @@ function [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
     imagePair,windowPair,sFrameArr,gtBoxArray,corners)
     % input: image pair number and window pair number
     % output: (x,y) coordinates for point correspondences of this window pair
-    
+    data1=[];
+    data2=[];
     % get the window in img1 and its corresponding window in img2
     w1 = windowPair;
     w2 = windowMatches{imagePair}(windowPair);

### 2015-12-12 p2/report/project_report.tex
more to report, cleaned up code sections

@@
 	showstringspaces=false,
-	frame=single
+	frame=single,
+	tabsize=3
 }
@@
 \setcounter{page}{1}
+\section{Project Summary}
+The purpose of this project was to perform object tracking in a time-series image set using many of the different image processing learned in class.
+
 \section{Integral Algorithms}
@@
 Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
+\\~\\
+\begin{minipage}{\textwidth}
 \begin{lstlisting}
@@
 \end{lstlisting}
+\end{minipage}
+
 This routine returns a non-normalized intensity image where strong intensities correspond to corner points in the image patch.
 Once this intensity image has been computed, it is passed to a thresholding routine where the coordinate points of these corners is determined.
-
+\\~\\
 \begin{minipage}{\textwidth}
@@
 
-assignment_set compute_bb_set(bounding_box a,b) {
+assignment_set compute_bb_set(bounding_box_a, bounding_box_b) {
 
@@
 	// point in bounding box b.
-	for (corner_a : a) {
-	for (corner_b : b) {
+	for (corner_a : bounding_box_a) {
+	for (corner_b : bounding_box_b) {
 		// Get the image patches around each corner point.
@@
 
-assignment_set compute_img_set(image a,b) {
+assignment_set compute_img_set(image_a, image_b) {
 
@@
 	// in image a against every bounding box in image b.
-	for (bounding_box_a : a) {
-	for (bounding_box_b : b) {
+	for (bounding_box_a : image_a) {
+	for (bounding_box_b : image_b) {
 
@@
 \end{minipage}
+\newpage
 \subsection{RANSAC}
+\subsubsection{Synopsis}
+Once the optimal bounding box correspondences have been determined, random sample consensus (RANSAC) can be used to estimate the translation of a bounding box between two images.
+RANSAC is a probabilistic, consensus-based algorithm which can be used to efficiently remove outliers from a set - in this problem space, outliers are ``bad'' corner points correspondences determined by the \texttt{compute\_bb\_set} function.
+\subsubsection{Implementation}
+\begin{minipage}{\textwidth}
+\begin{lstlisting}
+
+estimated_translation ransac(bounding_box_i, bounding_box_j,
+	num_iterations, threshold) {
+
+// Perform the inner-routine num\_iteartion times.
+for (i = 1 to num_iterations) {
+	// Get a random pair of corresponding corners
+	// from the bounding boxes.
+	corner_i = get_random_corner(bounding_box_i);
+	corner_j =
+	get_corresponding_corner(bounding_box_j, corner_i);
+
+	// Get the component-wise translation between these
+	// corresponding points.
+	translation = compute_translation(corner_i, corner_j);
+
+	inlier_count = 0;
+	max_inlier_count = 0, best_translation = 0;
+
+	for (corner : bounding_box_i) {
+		// Estimate where all the other corners should be based
+		// on the translation computed above.
+		estimated_corner = corner + translation;
+
+		// Get the actual correspondence point
+		actual_corner =
+			get_corresponding_corner(bounding_box_j, corner);
+
+		// If the estimated point is close to the actual point,
+		// consider the point an inlier.
+		distance = l2norm(actual_corner, estimated_corner);
+		if (distance < threshold) inlier_count++;
+	}
+
+	// Keep track of the best translation estimate.
+	if (inlier_count > max_inlier_count) {
+		max_inlier_count = inlier_count;
+		best_translation = translation;
+	}
+
+} return best_translation; }
+
+\end{lstlisting}
+\end{minipage}
 

### 2015-12-12 p2/report/project_report.tex
begun summary

@@
 \section{Project Summary}
-The purpose of this project was to perform object tracking in a time-series image set using many of the different image processing learned in class.
+The purpose of this project was to perform object tracking in a time-series image set using many of the different image processing techniques learned in class.
+Given an image taken at time $t_i$ and a bounding box around an object in the image, we estimate which bounding box in image $t_{i + 1}$ contains the same object.
+Once a correspondence is drawn between an object in these images, a motion estimate (translation) is calculated for that object.
 
-\section{Integral Algorithms}
+An object contained with a bounding box is characterized by its corner points; these corner points are obtained by running the Harris Corner Detection algorithm.
+To find correspondence sets between corner points and bounding boxes, the Munkres assignment algorithm is used.
+Finally, RANSAC is used to obtain an inlier-set of correspondences which are used in translation estimation.
+A description of these algorithms is found in Section \ref{algo}.
+
+\newpage
+\section{Integral Algorithms}\label{algo}
 \subsection{Harris Corner Detection}

### 2015-12-12 p2/matlab/main.m
ransac wrapper and display fixes. ransac demo done.

@@ -1,7 +1,7 @@
 %Parameters
-numOfFrames = 30; %set number frames 
+numOfFrames = 20; %set number frames 
 frameSkipRate = 1; %frame comparison distance
-frameindex = 7022;  %starting frame; range is 7022-7200
+frameindex = 7160;  %starting frame; range is 7022-7200
 filepath = '../frames/DaMultiview-seq';
 threshold = 235; %R threshold for harris corners
 alpha = 255; %controls how you want to choose corners at random
@@ -34,12 +34,15 @@ translations={};
 translationsByWindow = {};
 groundTruthTranslations;
 for i=1:size(cornerMatches,2)
-    disp(['running ransac on image: ',num2str(i)]);
+    disp(sprintf('running RANSAC on image pair: %d (frame %d to %d)'...
+        ,i,gtboxarray(sFrameArr(i),1)-1,gtboxarray(sFrameArr(i),1)));
     for j=1:size(windowMatches{i},1)
         [data1,data2] = ransacWrapper(cornerMatches,windowMatches,i,j,...
             sFrameArr,gtboxarray,corners);
-        [translations,translationsByWindow] = ransac(data1,data2,10000,1,...
+        [translations,translationsByWindow] = ransac(data1,data2,10000,2,...
             0.1,i,j,translations,translationsByWindow);
     end
+    ransacDisplay(cornerMatches,windowMatches,i,sFrameArr,...
+        gtboxarray,corners,translations);
 end
     

### 2015-12-12 p2/matlab/ransacDisplay.m

@@ -10,20 +10,25 @@ function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
     for i = 1:size(windowMatches{imagePair})
         [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
             imagePair,i,sFrameArr,gtboxarray,corners);
-        bb = gtboxarray(inds(i),:);
-        plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
-        text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
+        for k=1:length(inds)
+            bb = gtboxarray(inds(k),:);
+            plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
+            text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
+        end
         numDataPoints = size(data1,2);
         for j = 1:numDataPoints
             x_real = data2(2,j);
             y_real = data2(1,j);
             x_pred = data1(2,j)+translations{imagePair}{1}(2);
             y_pred = data1(1,j)+translations{imagePair}{1}(1);
-            plot(x_real,y_real,'g*');
             plot(x_pred,y_pred,'r*');
+            plot(x_real,y_real,'y*');
+            if x_pred==x_real && y_pred==y_real
+                plot(x_real,y_real, 'g*');
+            end
         end
     end
-    title(sprintf('frame %d',fnum));           
+    title(sprintf('RANSAC - frame %d to %d',fnum-1,fnum));           
     hold off; drawnow
 end
 

### 2015-12-12 p2/matlab/main.m
some early demo code

@@ -1,7 +1,7 @@
 %Parameters
-numOfFrames = 30; %set number frames 
+numOfFrames = 10; %set number frames 
 frameSkipRate = 1; %frame comparison distance
-frameindex = 7022;  %starting frame; range is 7022-7200
+frameindex = 7170;  %starting frame; range is 7022-7200
 filepath = '../frames/DaMultiview-seq';
 threshold = 235; %R threshold for harris corners
 alpha = 255; %controls how you want to choose corners at random
@@ -19,9 +19,14 @@ parseGroundTruthSupressed;
 [corners, sFrameArr] = phase1(numOfFrames, frameSkipRate, frameindex,...
     gtboxarray, filepath, threshold, alpha);
 
+
+
 %match corners and match boxes
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
+
+
+
 
 %Compute Accuracy
 accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);

### 2015-12-12 p2/report/project_report.tex

--- 2015-12-12 p2/report/project_report.tex
@@
 \setcounter{page}{1}
-\section{Project Summary}
-The purpose of this project was to perform object tracking in a time-series image set using many of the different image processing learned in class.
-
 \section{Integral Algorithms}
@@
 Below the implementation of the Harris corner detection algorithm in C-like pseudocode.
-\\~\\
-\begin{minipage}{\textwidth}
 \begin{lstlisting}
@@
 \end{lstlisting}
-\end{minipage}
-
 This routine returns a non-normalized intensity image where strong intensities correspond to corner points in the image patch.
 Once this intensity image has been computed, it is passed to a thresholding routine where the coordinate points of these corners is determined.
-\\~\\
+
 \begin{minipage}{\textwidth}

### 2015-12-12 p2/report/project_report.tex
input listings for important files

--- 2015-12-12 p2/report/project_report.tex
@@
 \usepackage {sectsty}
+\usepackage[T1]{fontenc}
 \usepackage{hyperref}
+\usepackage{underscore}
 \usepackage{graphicx}
+\usepackage[toc]{appendix}
 \graphicspath{ {img/} }
@@
 	keywordstyle=\ttfamily\color{blue}\footnotesize,
+	stringstyle=\ttfamily\color{purple},
 	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
@@
 	frame=single,
-	tabsize=3
+	tabsize=3,
+	breaklines=true,
+	breakautoindent=true,
 }
@@
 Finally, RANSAC is used to obtain an inlier-set of correspondences which are used in translation estimation.
-A description of these algorithms is found in Section \ref{algo}.
+A description of these algorithms and pseudocode implementation is found in Section \ref{algo}.
+The actual Matlab implementation of these functions is found in Appendix \ref{source}.
 
@@
 \]
-\includegraphics[width=\textwidth]{after_corner}
+\includegraphics[width=\textwidth]{aftercorner}
 \subsubsection{Implementation}
@@
 \begin{center}
-\fbox{\includegraphics[width=0.65\textwidth]{box_corners}}
+\fbox{\includegraphics[width=0.65\textwidth]{boxcorners}}
 \end{center}
@@
 
+\begin{appendices}
+\section{Source Code Listings}\label{source}
+% \lstinputlisting[escapechar=,language=Matlab,caption=blob2px.m,breaklines=true]{../matlab/blob2px.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=harris.m]{../matlab/harris.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=main.m, lastline=29]{../matlab/main.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=matcher.m, lastline=77]{../matlab/matcher.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=phase1.m]{../matlab/phase1.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=pruneMatrixScaled.m]{../matlab/pruneMatrixScaled.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=ransac.m]{../matlab/ransac.m}
+\lstinputlisting[escapechar=,language=Matlab,caption=SumOfSqaureDifferences.m]{../matlab/SumOfSqaureDifferences.m}
+\end{appendices}
+
 \end{document}

### 2015-12-12 p2/matlab/drawdemo.m
draw demo is (working)

@@ -31,6 +31,9 @@ for i=1:numOfFrames-1
 
         for k = 1 : numel(cs) / 2
             plot(cs(2,k), cs(1,k), 'r*');
+           
+        end
+        for k = 1 : numel(cs2) / 2
             plot(cs2(2,k), cs2(1,k), 'r*');
         end
         plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');

### 2015-12-12 p2/report/project_report.tex
section for intermediate output

@@
 
+\section{Intermediate Results}
+In this section we include results from the various modules implemented in this program.
+These results were used to verify correctness of each particular unit of code, as well as tune the entire program to produce accurate results.
+\subsection{Harris Corner Detection}
+To test our implementation of the Harris Corner Detection algorithm, we used various images containing geometric scenes.
+For example, below is a skyscraper facade passed through our routine.
+As expected, the corner points on each window have very high intensity values and the edges in the image have very low intensity values.
+\begin{center}
+\fbox{\includegraphics[width=150pt, height=150pt]{harrisinput}}
+\fbox{\includegraphics[width=150pt, height=150pt]{harrisoutput}}
+\end{center}
+
+\newpage
 \begin{appendices}

### 2015-12-12 p2/matlab/drawdemo.m
pics and demos

@@ -1,5 +1,20 @@
-%for each image pair
+%display the corners and bounding box matches between images
+%so for each image the neighboring images are compared (i.e 1 is compared
+%with 2, 2 is compared with 3, and so on)
+%This code segment will display the neighboring pictures in a figure. The
+%picture on the left will be the first neighboring image and the
+%picture on the right will be the second neighboring image. They pictures
+%will show that bounding boxes that our code matched (they aren't always
+%right). It also shows the corners it used to match the boxes in red.
+%below are some parameters you can use to configure what is printed out.
+%number of image pair you want to print out
+imagesToPrint = 1; %number of image pair examples you'd like to display
+boxesPerImagePair = 2; %number of bounding boxes and corner examples
+                       %to display per image pair demo
 for i=1:numOfFrames-1
+   if ( i > imagesToPrint )
+       break;
+   end
    dims1 = size(windowMatches{i});
    filename = strcat(filepath, num2str(frameindex+i-1));
    filename = strcat(filename, '.png');
@@ -10,6 +25,9 @@ for i=1:numOfFrames-1
    dimi1 = size(i1);
    
    for j=1:dims1(1)
+        if (j > boxesPerImagePair)
+           break;
+        end
         figure;
         imagesc([i1 i2]);
         

### 2015-12-12 p2/matlab/main.m

@@ -1,6 +1,8 @@
 %Parameters
 numOfFrames = 10; %set number frames 
-frameSkipRate = 1; %frame comparison distance
+frameSkipRate = 1; %DON"T CHANGE THIS! THE PROGRAM ONLY FUNCTIONS 
+                    %IF IT IS SET TO 1
+                    %frame comparison distance
 frameindex = 7170;  %starting frame; range is 7022-7200
 filepath = '../frames/DaMultiview-seq';
 threshold = 235; %R threshold for harris corners
@@ -25,8 +27,8 @@ parseGroundTruthSupressed;
 [cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
-
-
+%open up drawdemo.m to learn about what it is and how to configure it
+drawdemo;
 
 %Compute Accuracy
 accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);

### 2015-12-12 p2/matlab/main.m
ransac demo done

@@ -38,9 +38,8 @@ disp( sprintf( ...
 translations={};
 translationsByWindow = {};
 groundTruthTranslations;
+disp(sprintf('Running RANSAC on all windows in all images.'));
 for i=1:size(cornerMatches,2)
-    disp(sprintf('running RANSAC on image pair: %d (frame %d to %d)'...
-        ,i,gtboxarray(sFrameArr(i),1)-1,gtboxarray(sFrameArr(i),1)));
     for j=1:size(windowMatches{i},1)
         [data1,data2] = ransacWrapper(cornerMatches,windowMatches,i,j,...
             sFrameArr,gtboxarray,corners);

### 2015-12-12 p2/matlab/ransacDisplay.m

@@ -7,28 +7,33 @@ function [] = ransacDisplay(cornerMatches,windowMatches,imagePair,...
     im = imread(fname);
     imagesc(im); axis equal
     hold on
-    for i = 1:size(windowMatches{imagePair})
+    for i = 1:size(windowMatches{imagePair});
+        w1 = i;
+        w2 = windowMatches{imagePair}(w1);
         [data1,data2] = ransacWrapper(cornerMatches,windowMatches,...
             imagePair,i,sFrameArr,gtboxarray,corners);
-        for k=1:length(inds)
-            bb = gtboxarray(inds(k),:);
+        for k = 1:length(inds)
+            bb = gtboxarray(inds(i),:);
             plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
             text(mean(bb([3 5])),mean(bb([4 6])),sprintf('%d',bb(2)),'Color','y');
         end
         numDataPoints = size(data1,2);
         for j = 1:numDataPoints
-            x_real = data2(2,j);
-            y_real = data2(1,j);
-            x_pred = data1(2,j)+translations{imagePair}{1}(2);
-            y_pred = data1(1,j)+translations{imagePair}{1}(1);
-            plot(x_pred,y_pred,'r*');
-            plot(x_real,y_real,'y*');
-            if x_pred==x_real && y_pred==y_real
-                plot(x_real,y_real, 'g*');
+            if cornerMatches{imagePair}{w1,w2}(j) ~= 0
+                x_real = data2(2,j);
+                y_real = data2(1,j);
+                x_pred = data1(2,j)+translations{imagePair}{1}(2);
+                y_pred = data1(1,j)+translations{imagePair}{1}(1);
+                plot(x_pred,y_pred,'r*');
+                plot(x_real,y_real,'y*');
+                if x_pred == x_real && y_pred == y_real
+                    plot(x_real,y_real, 'g*');
+                end
             end
         end
     end
     title(sprintf('RANSAC - frame %d to %d',fnum-1,fnum));           
     hold off; drawnow
 end
+
 

### 2015-12-12 p2/matlab/main.m
now the ransac demo is done

@@ -37,6 +37,8 @@ disp( sprintf( ...
     (accuracy)*100 ) );
 
 %Ransac to get translations between matched windows
+h = figure;
+set(h,'name','RANSAC','numbertitle','off');
 translations={};
 translationsByWindow = {};
 groundTruthTranslations;

### 2015-12-12 p2/report/project_report.tex
intermediate output for harris

@@
 \end{center}
+~\\
+This window image is very idealistic; the corners in this image are distinctive and well-defined.
+We have found that this corner detection algorithm also works well on less-ideal input.
+Here is the result when the algorithm is run on the first bounding box in the image 7022:
+\begin{center}
+\fbox{\includegraphics[scale=.4]{woman}}
+\fbox{\includegraphics[scale=.4]{womanharris}}
+\end{center}
+The algorithm does a good job of suppressing the uniform regions of the image (the woman's jacket, shirt, and pants) and highlights regions of high contrast (the woman's hand against her jacket, hair against her head).
 

### 2015-12-12 p2/matlab/main.m
more demo stuff

@@ -24,17 +24,26 @@ parseGroundTruthSupressed;
 
 
 %match corners and match boxes
-[cornerMatches, windowMatches] = matcher (corners, sFrameArr, numOfFrames,...
+[cornerMatches, windowMatches,affineWindowMatchMatrices] = ...
+    matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
 %open up drawdemo.m to learn about what it is and how to configure it
 drawdemo;
 
-%Compute Accuracy
+%Compute Accuracy Measurements
 accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);
 disp( sprintf( ...
     'Windows were correctly matched between sequential images %2.2f%% of the time.',...
     (accuracy)*100 ) );
+numberOfAffineWindowMatchMaricesToShow = 1;
+for i = 1:numOfFrames-1
+    if ( i > numberOfAffineWindowMatchMaricesToShow )
+       break; 
+    end
+    figure;
+    surf(affineWindowMatchMatrices{i});
+end
 
 %Ransac to get translations between matched windows
 translations={};
@@ -51,4 +60,6 @@ for i=1:size(cornerMatches,2)
     ransacDisplay(cornerMatches,windowMatches,i,sFrameArr,...
         gtboxarray,corners,translations);
 end
+
+
     

### 2015-12-12 p2/matlab/matcher.m

@@ -1,4 +1,5 @@
-function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFrames, ...
+function [ cornerMatches, windowMatches, affineWindowMatchMatrices ]...
+    = matcher( corners, sFrameArr, numOfFrames, ...
     gtboxarray, filepath, frameindex, cornerpatchx, cornerpatchy)
 
     %cornerMatches = [];%zeros(numOfFrames-1);
@@ -99,7 +100,7 @@ function [ cornerMatches, windowMatches ] = matcher( corners, sFrameArr, numOfFr
         end
         cornerMatches(frame) = {cornerMatchesByWindow};
         
-        
+        affineWindowMatchMatrices(frame) = {boxmatchmatrix};
         
         [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
         

### 2015-12-12 p2/matlab/main.m
demo stuff

@@ -24,7 +24,7 @@ parseGroundTruthSupressed;
 
 
 %match corners and match boxes
-[cornerMatches, windowMatches,affineWindowMatchMatrices] = ...
+[cornerMatches, windowMatches,affinityWindowMatchMatrices] = ...
     matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
@@ -36,13 +36,13 @@ accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);
 disp( sprintf( ...
     'Windows were correctly matched between sequential images %2.2f%% of the time.',...
     (accuracy)*100 ) );
-numberOfAffineWindowMatchMaricesToShow = 1;
+numberOfAffinityWindowMatchMaricesToShow = 1;
 for i = 1:numOfFrames-1
-    if ( i > numberOfAffineWindowMatchMaricesToShow )
+    if ( i > numberOfAffinityWindowMatchMaricesToShow )
        break; 
     end
     figure;
-    surf(affineWindowMatchMatrices{i});
+    surf(affinityWindowMatchMatrices{i});
 end
 
 %Ransac to get translations between matched windows

### 2015-12-12 p2/matlab/matcher.m

@@ -1,4 +1,4 @@
-function [ cornerMatches, windowMatches, affineWindowMatchMatrices ]...
+function [ cornerMatches, windowMatches, affinityWindowMatchMatrices ]...
     = matcher( corners, sFrameArr, numOfFrames, ...
     gtboxarray, filepath, frameindex, cornerpatchx, cornerpatchy)
 
@@ -100,7 +100,7 @@ function [ cornerMatches, windowMatches, affineWindowMatchMatrices ]...
         end
         cornerMatches(frame) = {cornerMatchesByWindow};
         
-        affineWindowMatchMatrices(frame) = {boxmatchmatrix};
+        affinityWindowMatchMatrices(frame) = {boxmatchmatrix};
         
         [aboxes,cboxes] = assignmentoptimal(boxmatchmatrix);
         

### 2015-12-12 p2/matlab/main.m
Code is "Finished"
We still need to clean up and comment the code. Maybe verify it a bit too. Mostly just need to start focusing on the report though.

@@ -28,6 +28,8 @@ parseGroundTruthSupressed;
     matcher (corners, sFrameArr, numOfFrames,...
     gtboxarray, filepath, frameindex, cornerPatchSizeX, cornerPatchSizeY);
 
+%here are some results of the matching
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %open up drawdemo.m to learn about what it is and how to configure it
 drawdemo;
 
@@ -36,6 +38,7 @@ accuracy = Acurrator(windowMatches,gtboxarray,sFrameArr);
 disp( sprintf( ...
     'Windows were correctly matched between sequential images %2.2f%% of the time.',...
     (accuracy)*100 ) );
+%affinity matrices
 numberOfAffinityWindowMatchMaricesToShow = 1;
 for i = 1:numOfFrames-1
     if ( i > numberOfAffinityWindowMatchMaricesToShow )

### 2015-12-12 p2/matlab/ncc.m

@@ -1,42 +1,0 @@
-function [ ncc ] = ncc( p1,p2,pp1,pp2,x,y,w1,w2 )
-    
-    
-    pp1(1) = pp1(1)-y/2;
-    pp1(2) = pp1(2)-x/2;
-    pp2(1) = pp2(1)-y/2;
-    pp2(2) = pp2(2)-x/2;
-    
-    dim1 = size(p1);
-    dim2 = size(p2);
-    
-    w1xmin = w1(3);
-    w1ymin = w1(4);
-    w2xmin = w2(3);
-    w2ymin = w2(4);
-    
-    
-    p1x = pp1(2);
-    p1y = pp1(1);
-    p2x = pp2(2);
-    p2y = pp2(1);
-    
-    ip1x = w1xmin+p1x;
-    ip1y = w1ymin+p1y;
-    ip2x = w2xmin+p2x;
-    ip2y = w2ymin+p2y;
-
-
-    ncc1 = 0;
-    ncc2 = 0;
-    ncc3 = 0;
-    ncc = 0;
-    
-    for i=1:x
-      for j=1:y
-        ncc1 = ncc1 + (p1(ip1y+i,ip1x+j)*p2(ip2y+i,ip2x+j));
-        ncc2 = ncc2 + (p1(ip1y+i,ip1x+j) * p1(ip1y+i,ip1x+j));
-        ncc3 = ncc3 + (p2(ip2y+i,ip2x+j) * p2(ip2y+i,ip2x+j));
-        ncc = ncc + ncc1/sqrt(ncc2 * ncc3);
-      end
-    end
-end

### 2015-12-12 p2/report/project_report.tex
added matching subsection
progress on matching section

@@
 \pagestyle{fancy}
-\renewcommand{\rightmark}{}
+% \renewcommand{\rightmark}{}
 
@@
 
+\subsection{Matching}
+Object matching between bounding boxes works consistently with 75\% to 95\% accuracy -- see the next section for performance metrics and accuracy measurements.
+Pictured below is a bounding box correspondence computed by \texttt{matcher.m} in the \hyperref[source]{Source Code Listing} section.
+With input images 7170 and 7171, the matching routine correctly corresponded box six to box six using the Harris corner points indicated by the red star points in the image.
+\begin{center}
+\fbox{\includegraphics[width=\textwidth]{"matchresults-with-corners(7170 to 7171, box id 6 match)"}}
+\end{center}
+~\\
+Using simple two-image test cases allowed us to further tune various parameters in our modules to improve overall matching accuracy.
+We found that the image patch size used in the SSD scoring portion of the matching process made a significant difference in accuracy: if the patch size was too small or too large, accuracy significantly dropped.
+A patch size of 12 pixels by 12 pixels seemed to yield the best results.
+
 \newpage

### 2015-12-12 p2/report/project_report.tex
'final stuff'

--- 2015-12-12 p2/report/project_report.tex
@@
 
+\subsection{Matching}
+
+\section{Results}
+
+\subsection{Matching Results}
+We wrote our code to look for box matches for an image with the image that preceded it in the set.
+For example, we would look for box matching between image 7170 and image 7171.
+When running it on a series of 10 images starting with 7170 and ending with 7180, our program matched boxes correctly 92.59\% of the time.
+~\\~\\
+When running the program on images earlier on in the image data set, like 7022, the program matched boxes correctly around 75\% of the time.
+The explanation for this is in the beginning the people cluster together and many of them are wearing similar clothing so it hard for the program to distinguish features.
+Towards the end of the image set the people begin to spread out again and it becomes easy for the program to accurately match boxes again.
+~\\~\\~\\
+\begin{LARGE}
+	THIS SECTION SHOUILD BE MOVED INTO THE INTERMEDIATE RESULTS SECTION ABOVE AS STATED BY THE RUBRIC.
+\end{LARGE}
+Shown below is a graph of the affinity matrix for matching boxes between image 7170 and 7171.
+The value at each location is the cost of pairing box x in image 7170 with box y in 7171; where a lower cost is better.
+~\\
+\begin{center}
+\fbox{\includegraphics[scale=.8]{affinitymatrix-box-matching-example-7170-to-7171.png}}
+\end{center}
+~\\~\\~\\
+Be aware that the program can be ran, accuracy can be computed, and the affinity matrices can be displayed by configuring the settings in main.m and by running the main.m script.
+Running the main.m script will also show some intermediate results to help demonstrate what the program does.
 \newpage

### 2015-12-12 p2/matlab/SumOfSqaureDifferences.m

@@ -1,10 +1,7 @@
 function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
-    %make this a long?    
-    
-
     
     ssd = double(0);
-    t = 0;
+    
     p1(1) = p1(1)-y/2;
     p1(2) = p1(2)-x/2;
     p2(1) = p2(1)-y/2;
@@ -37,7 +34,6 @@ function [ ssd ] = SumOfSqaureDifferences( i1,i2,p1,p2,x,y,w1,w2 )
     for i=1:x
       for j=1:y
           for k=1
-                %check this because there was an index out of bounds error
                 if ~(ip1y + j> dim1(1) || ip1x + i > dim1(2) || ...
                        ip2y + j > dim2(1) || ip2x + i > dim2(2))
                    

### 2015-12-12 p2/matlab/matcher.m

@@ -1,10 +1,20 @@
 function [ cornerMatches, windowMatches, affinityWindowMatchMatrices ]...
     = matcher( corners, sFrameArr, numOfFrames, ...
     gtboxarray, filepath, frameindex, cornerpatchx, cornerpatchy)
+%This function takes in the images, he harris corners, and the bounding-boxes
+%and it tries to match boxes in an image with the image preceding it for a 
+%series of images. 
+%It pulls bounding box information from gtboxarray.
+%It pulls the images directly from the .png files.
+%It pulls the Harris Corners from corners.
+%It outputs the corner matches that are deemed optimal between all 
+%combinations of boxes when trying to match boxes between
+%images.(cornerMatches)
+%It also outupts the window matches in windowMatches.
+%IT also outputs the affinity matrix it uses to determine windowMatches and
+%that is stored in affinityWindowMatchMatrices
 
-    %cornerMatches = [];%zeros(numOfFrames-1);
-    %windowMatches = [];%zeros(numOfFrames-1);
-    
+
 %match up corners
     for frame = 1:numOfFrames-1
         frame1 = frame;
@@ -51,38 +61,6 @@ function [ cornerMatches, windowMatches, affinityWindowMatchMatrices ]...
        
                 cornermatchmatrix = zeros(i1corners,i2corners);
                 
-                   %{
-                    figure;
-                    imagesc(i1);
-
-                    hold on
-                    cs = corners{frame1boxstart+b1-1}(:,:);
-                    cs(1,:) = cs(1,:)+w1(4);
-                    cs(2,:) = cs(2,:)+w1(3);
-                    cs1 = cs;
-                    bb = w1;
-                    for k = 1 : numel(cs) / 2
-                        plot(cs(2,k), cs(1,k), 'r*');
-                        plot(bb([3 3 5 5 3]),bb([4 6 6 4 4]),'g-');
-                    end
-                    hold off;
-                    
-                    figure;
-                    imagesc(i1);
-
-                    hold on
-                    cs = corners{frame2boxstart+b2-1}(:,:);
-                    bb = w2;
-                    cs(1,:) = cs(1,:)+w2(4);
-                    cs(2,:) = cs(2,:)+w2(3);
-                    cs2 = cs;
-                    for k = 1 : numel(cs) / 2
-                        plot(cs(2,k), cs(1,k), 'r*');
[…]

### 2015-12-12 p2/report/project_report.tex

@@
 \subsection{Matching}
+Object matching between bounding boxes works consistently with 75\% to 95\% accuracy -- see the next section for performance metrics and accuracy measurements.
+Pictured below is a bounding box correspondence computed by \texttt{matcher.m} in the \hyperref[source]{Source Code Listing} section.
+With input images 7170 and 7171, the matching routine correctly corresponded box six to box six using the Harris corner points indicated by the red star points in the image.
+\begin{center}
+\fbox{\includegraphics[width=\textwidth]{"matchresults-with-corners(7170 to 7171, box id 6 match)"}}
+\end{center}
+~\\
+Using simple two-image test cases allowed us to further tune various parameters in our modules to improve overall matching accuracy.
+We found that the image patch size used in the SSD scoring portion of the matching process made a significant difference in accuracy: if the patch size was too small or too large, accuracy significantly dropped.
+A patch size of 12 pixels by 12 pixels seemed to yield the best results.
 
